---
title: "Occurrence"
author: "Nat"
date: "2024-03-11"
output: html_document
---

# Load dataframes and packages

```{r}
library(tidyverse)


# plots with Card#B removed, ask Anya what they are
regen <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/Regen_2023_ALL.csv")
site <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/site.csv")
GIS <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/from_GIS.csv")
GIS1 <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/from_GIS.csv")
clipGis <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/PossiblePlot.csv")
internal <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/Internal.csv")
basal <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/BasalArea.csv")
```

#formatting data

```{r}
# Fill in blank species, NR = no regen
regen$Species <- sub("^$", "NR", regen$Species)
regen$Species <- sub("ACT", "NonCon", regen$Species)
regen$Species <- sub("AT", "NonCon", regen$Species)
regen$Species <- sub("SW", "Spruce", regen$Species)
regen$Species <- sub("SE", "Spruce", regen$Species)
regen$Species <- sub("SX", "Spruce", regen$Species)


# get rid of unnecessary columns
regen<- regen %>% 
  select(Card,Quandrant,Species,Notes,x0,x10,x30,x130) 

# new column for species by plot
regen$Plot_Sp <- paste(regen$Card, regen$Species, sep = "")

#new column for total of seedlings per wedge by species
regen<- regen%>% 
  mutate(total = rowSums(cbind(regen$x0,regen$x10,regen$x30,regen$x130),na.rm=TRUE))

#combine different wedges by height class

regen_only_total <- regen %>% 
  group_by(Card, Species, Plot_Sp) %>% 
  summarise(across(total, sum))

regen_only_x0 <- regen %>% 
  group_by(Plot_Sp) %>% 
  summarise(x0 = sum(x0, na.rm = TRUE))

regen_only_x10 <- regen %>% 
  group_by(Plot_Sp) %>% 
  summarise(x10 = sum(x10, na.rm = TRUE))

regen_only_x30 <- regen %>% 
  group_by(Plot_Sp) %>% 
  summarise(x30 = sum(x30, na.rm = TRUE))

regen_only_x130 <- regen %>% 
  group_by(Plot_Sp) %>% 
  summarise(x130 = sum(x130, na.rm = TRUE))

#combine into 1 data frame

regen_all <- full_join(regen_only_total, regen_only_x0, by = "Plot_Sp") %>% 
  full_join(regen_only_x10, by = "Plot_Sp") %>% 
  full_join(regen_only_x30, by = "Plot_Sp") %>%
  full_join(regen_only_x130, by = "Plot_Sp")

# now i want to have columns for each species
regen_all$FDI_total <- ifelse(regen_all$Species == "FDI", regen_all$total, 0)
regen_all$FDI_x0 <- ifelse(regen_all$Species == "FDI", regen_all$x0, 0)
regen_all$FDI_x10 <- ifelse(regen_all$Species == "FDI", regen_all$x10, 0)
regen_all$FDI_x30 <- ifelse(regen_all$Species == "FDI", regen_all$x30, 0)
regen_all$FDI_x130 <- ifelse(regen_all$Species == "FDI", regen_all$x130, 0)
regen_all$PLI_total <- ifelse(regen_all$Species == "PLI", regen_all$total, 0)
regen_all$PLI_x0 <- ifelse(regen_all$Species == "PLI", regen_all$x0, 0)
regen_all$PLI_x10 <- ifelse(regen_all$Species == "PLI", regen_all$x10, 0)
regen_all$PLI_x30 <- ifelse(regen_all$Species == "PLI", regen_all$x30, 0)
regen_all$PLI_x130 <- ifelse(regen_all$Species == "PLI", regen_all$x130, 0)
regen_all$NonCon_total <- ifelse(regen_all$Species == "NonCon", regen_all$total, 0)
regen_all$NonCon_x0 <- ifelse(regen_all$Species == "NonCon", regen_all$x0, 0)
regen_all$NonCon_x10 <- ifelse(regen_all$Species == "NonCon", regen_all$x10, 0)
regen_all$NonCon_x30 <- ifelse(regen_all$Species == "NonCon", regen_all$x30, 0)
regen_all$NonCon_x130 <- ifelse(regen_all$Species == "NonCon", regen_all$x130, 0)
regen_all$Spruce_total <- ifelse(regen_all$Species == "Spruce", regen_all$total, 0)
regen_all$Spruce_x0 <- ifelse(regen_all$Species == "Spruce", regen_all$x0, 0)
regen_all$Spruce_x10 <- ifelse(regen_all$Species == "Spruce", regen_all$x10, 0)
regen_all$Spruce_x30 <- ifelse(regen_all$Species == "Spruce", regen_all$x30, 0)
regen_all$Spruce_x130 <- ifelse(regen_all$Species == "Spruce", regen_all$x130, 0)


# remove NR rows for plots that have other species present
regen_all <- regen_all %>% 
  group_by(Card) %>% 
  mutate(has_nr = any(Species == "NR"), num_rows = n()) %>% 
  filter(num_rows == 1 | !(has_nr & Species == "NR")) %>% 
  select(-has_nr, -num_rows)


## Check if we removed the correct values
# look into plots that have counts larger than zero. Seems like there should have been a species recorded
#(plots 1505, 1529, 1567, 1647, 1739, 2318)
regen_retained <- regen_all %>% 
  group_by(Card) %>% 
  mutate(has_nr = any(Species == "NR"), num_rows = n()) %>% 
  filter(num_rows == 1 | !(has_nr & Species == "NR")) %>% 
  select(-has_nr, -num_rows)

## Create dataframe with removed rows
regen_removed <- regen_all %>%
  anti_join(regen_retained, by = c("Card", "Species"))

# combine rows for same plot
regen_combo <- regen_all %>%
  group_by(Card) %>%
  summarize(SpeciesAll = paste(Species, collapse = ", "),
            total_count = sum(total),
            total_tph = total_count*200,
            total_x0 = sum(x0),
            total_x10 = sum(x10),
            total_x30 = sum(x30),
            total_x130 = sum(x130),
            FDI_count = sum(FDI_total),
            FDI_tph = FDI_count*200,
            FDI_x0 = sum(FDI_x0),
            FDI_x10 = sum(FDI_x10),
            FDI_x30 = sum(FDI_x30),
            FDI_x130 = sum(FDI_x130),
            PLI_count = sum(PLI_total),
            PLI_tph = PLI_count*200,
            PLI_x0 = sum(PLI_x0),
            PLI_x10 = sum(PLI_x10),
            PLI_x30 = sum(PLI_x30),
            PLI_x130 = sum(PLI_x130),
            NonCon_count = sum(NonCon_total),
            NonCon_x0 = sum(NonCon_x0),
            NonCon_x10 = sum(NonCon_x10),
            NonCon_x30 = sum(NonCon_x30),
            NonCon_x130 = sum(NonCon_x130),
            Spruce_count = sum(Spruce_total),
            Spruce_x0 = sum(Spruce_x0),
            Spruce_x10 = sum(Spruce_x10),
            Spruce_x30 = sum(Spruce_x30),
            Spruce_x130 = sum(Spruce_x130)) %>% 
  ungroup()



# I could add TPH, but I don't think I will. It's just multiplying everything by 200
##adding it now for total counts

# export dataframe
#write.csv(regen_combo, "C:/Users/nmac2000/Documents/regen project/Data/cleaned_counts_021224.csv")
```

#Add the GIS data

```{r}
# add GIS data
regen$Card <- as.integer(regen$Card)
regen_copy <- regen #don't
regen_copy <- regen_copy %>% 
  rename(SampleSite_ID = Card)
clipped_plots <- semi_join(clipGis, regen_copy, "SampleSite_ID")
forgotten_plots <- anti_join(regen_copy, clipped_plots, "SampleSite_ID")

clipGIS1 <- clipGis %>% 
  select(SampleSite_ID)
forgotten_plots <- forgotten_plots %>% 
  select(SampleSite_ID)
clipGis <- full_join(clipGIS1,forgotten_plots, "SampleSite_ID")

GIS <- semi_join(GIS, clipGis, "SampleSite_ID")
GIS$Card <- as.integer(GIS$SampleSite_ID)
regen_combo$Card <- as.integer(regen_combo$Card, na.rm=TRUE)

GIS$Species_1 <- sub("\\bSX\\b", "Spruce", GIS$Species_1)
GIS$Species_1 <- sub("\\bS\\b", "Spruce", GIS$Species_1)
GIS$Species_1 <- sub("\\bSE\\b", "Spruce", GIS$Species_1)
GIS$Species_1 <- sub("\\bPL\\b", "PLI", GIS$Species_1)
GIS$Species_1 <- sub("\\bFD\\b", "FDI", GIS$Species_1)
GIS$Species_1 <- sub("\\bPA\\b", "PLI", GIS$Species_1)

#write.csv(GIS, "C:/Users/nmac2000/Documents/regen project/Data/possibleplots_GIS.csv")

regen_GIS <- left_join(regen_combo,GIS, by = "Card") %>% 
  ungroup()

#write.csv(regen_GIS, "C:/Users/nmac2000/Documents/regen project/Data/regen_GIS.csv")

#trying to get some stuff to work on arc
#GIS_filter <- regen_GIS %>% 
 # filter(!is.na(Latitude)) 
#sf_data <- st_as_sf(GIS_filter, coords = c("Longitude", "Latitude"), crs = 3005)
#st_write(sf_data, "C:/Users/nmac2000/Documents/regen project/Data/cleaned_counts_021224.shp", driver = "ESRI Shapefile")
```

# some plots (not that useful)

```{r}
#plots###############################################################################################
head(regen_GIS)
names(regen_GIS)


## Making plots. Need to make them look better


ggplot(regen_GIS, aes(x=PARENT_SOILS,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=Fire_Severity_1,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=Zone,y=total_count)) +
  geom_boxplot()

#will maybe have to combine some of these (what is PL)
ggplot(regen_GIS, aes(x=Species_1,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=DRAIN_1,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=DRAIN_1)) +
  geom_boxplot(aes(y=total_count), color="blue",position = "dodge") +
  geom_boxplot(aes(y=PLI_count), color = "red", position = "dodge")

ggplot(regen_GIS, aes(x=Solar_Radiation)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=TWI)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5) 

ggplot(regen_GIS, aes(x=COFRAG_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

#do as boxplot
ggplot(regen_GIS, aes(x=Aspect)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Severity_Patch_Size_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Age_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)  

ggplot(regen_GIS, aes(x=Height_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Crown_Closure_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Disturbance_Date_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Distance_to_Perimeter)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)
```

# deliverables for Anya
making tables for different categorical variables and seeing how they have been sampled

```{r}
table(GIS$SOILNAME_1)
table(regen_GIS$SOILNAME_1)


compare_tables <- function(table1, table2, driver_column) {
  # Convert factor columns to characters
  table1[[driver_column]] <- as.character(table1[[driver_column]])
  table2[[driver_column]] <- as.character(table2[[driver_column]])
  
  # Use count function to get counts for each table
  count_table1 <- count(table1, !!as.name(driver_column))
  count_table2 <- count(table2, !!as.name(driver_column))
  
  # Combine counts using full join
  comparison_df <- full_join(count_table1, count_table2, by = driver_column)
  
  # Replace NAs with 0 in the count columns
  comparison_df[is.na(comparison_df)] <- 0
  
  # Return the comparison table
  return(comparison_df)
}

# usage:
driver_column_name <- c("Fire_Severity_1")  
result <- compare_tables(GIS, regen_GIS, driver_column_name)
print(result)


BEC_comparison <- compare_tables(GIS, regen_GIS, "Zone")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
ParentSoil_comparison <- compare_tables(GIS, regen_GIS, "PARENT_SOILS")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
SoilName_comparison  <- compare_tables(GIS, regen_GIS, "SOILNAME_1")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
Texture_comparison <- compare_tables(GIS, regen_GIS, "TEXTURE_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
Drainage_comparison  <- compare_tables(GIS, regen_GIS, "DRAIN_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
#two different rows with 0s
Cofrag_comparison  <- compare_tables(GIS, regen_GIS, "COFRAG_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100)
FireYear_comparison  <- compare_tables(GIS, regen_GIS, "Fire_Year_1")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%  
  filter(row_number() <= n()-1)
FireNum_comparison  <- compare_tables(GIS, regen_GIS, "Fire_Number_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/total_plots*100) %>% 
  filter(row_number() <= n()-1)
FireSeverity_comparison  <- compare_tables(GIS, regen_GIS, "Fire_Severity_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)




Overstory_comparison  <- compare_tables(GIS, regen_GIS, "Species_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
# Combine some of the Species for overstory
# PLI <- PL
# FDI <- FD
# Spruce <- SE, SX
# ??? <- B, EP, S


#
CrownClosure_comparison  <- compare_tables(GIS, regen_GIS, "Crown_Closure_1")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) 
Disturbance_comparison  <- compare_tables(GIS, regen_GIS, "Disturbance_Type_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
Subzone_comparison  <- compare_tables(GIS, regen_GIS, "Subzone")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)

```


# Continuation of deliverables for Anya
this looks at occurrence and basic stocking for some of the categorical data
```{r}
#deliverables#################################################
#Anya wants conifer count
#Fire severity
regen_FS <- regen_GIS %>% 
  select(Card:Spruce_x130,Fire_Severity_1) %>% 
  group_by(Fire_Severity_1) %>% 
  filter(!is.na(Fire_Severity_1))

regen_FS$Con_count <- regen_FS$FDI_count + regen_FS$PLI_count + regen_FS$Spruce_count
regen_FS$Con_tph <- regen_FS$Con_count*200

options(pillar.sigfig = 6) 

regen_FS %>% 
  summarise(across(c(31,32), sd))

regen_FS %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_FS %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_FS) +
  geom_histogram(aes(x = Con_count, fill = Fire_Severity_1), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Fire_Severity_1))

#write.csv(FireSeverity_comparison, "C:/Users/nmac2000/Documents/regen project/Data/FireSeverity.csv")

#BEC zones
regen_BEC <- regen_GIS %>% 
  select(Card:Spruce_x130,Zone) %>% 
  group_by(Zone) %>% 
  filter(!is.na(Zone))

regen_BEC$Con_count <- regen_BEC$FDI_count + regen_BEC$PLI_count + regen_BEC$Spruce_count
regen_BEC$Con_tph <- regen_BEC$Con_count*200

options(pillar.sigfig = 6) 

regen_BEC %>% 
  summarise(across(c(31,32), sd))

regen_BEC %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_BEC %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_BEC) +
  geom_histogram(aes(x = Con_count, fill = Zone), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Zone))


## add subzone
regen_subzone <- regen_GIS %>% 
  select(Card:Spruce_x130,Zone,Subzone) %>% 
  group_by(Zone,Subzone) %>% 
  filter(!is.na(Zone))

regen_subzone$Con_count <- regen_BEC$FDI_count + regen_BEC$PLI_count + regen_BEC$Spruce_count
regen_subzone$Con_tph <- regen_BEC$Con_count*200

options(pillar.sigfig = 6) 

regen_subzone %>% 
  summarise(across(c(31,32), sd))

regen_subzone %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_subzone %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_subzone) +
  geom_histogram(aes(x = Con_count, fill = Subzone), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Subzone))

#Overstory


regen_Overstory <- regen_GIS %>% 
  select(Card:Spruce_x130,Species_1) %>% 
  group_by(Species_1) %>% 
  filter(!is.na(Species_1))

regen_Overstory$Species_1 <- sub("\\bSX\\b", "Spruce", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bS\\b", "Spruce", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bSE\\b", "Spruce", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bPL\\b", "PLI", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bFD\\b", "FDI", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bPA\\b", "PLI", regen_Overstory$Species_1)

regen_Overstory$Con_count <- regen_Overstory$FDI_count + regen_Overstory$PLI_count + regen_Overstory$Spruce_count
regen_Overstory$Con_tph <- regen_Overstory$Con_count*200

options(pillar.sigfig = 6) 

regen_Overstory %>% 
  summarise(across(c(31,32), sd))

regen_Overstory %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_Overstory %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_Overstory) +
  geom_histogram(aes(x = Con_count, fill = Species_1), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Species_1))
```

#Which plots have unknown burn severity
```{r}
for_table <- regen_GIS %>% 
  filter(Fire_Severity_1 == "Unknown") %>% 
  select(Card, Fire_Year_1, Fire_Year_2, Fire_Severity_1, Fire_Severity_2, Fire_Number_1, Fire_Number_2, Longitude, Latitude)

#write.csv(for_table, "C:/Users/nmac2000/Documents/regen project/Data/Unknown_Severity_Measured_Plots.csv")

```

# Looking at wedge data (Bianca said this isnt useful)
```{r}
#Wedges###############################
# now i want to have columns for each species
regen_wedge <- regen
regen_wedge$FDI_total <- ifelse(regen_wedge$Species == "FDI", regen_wedge$total, 0)
regen_wedge$FDI_x0 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x0, 0)
regen_wedge$FDI_x10 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x10, 0)
regen_wedge$FDI_x30 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x30, 0)
regen_wedge$FDI_x130 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x130, 0)
regen_wedge$PLI_total <- ifelse(regen_wedge$Species == "PLI", regen_wedge$total, 0)
regen_wedge$PLI_x0 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x0, 0)
regen_wedge$PLI_x10 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x10, 0)
regen_wedge$PLI_x30 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x30, 0)
regen_wedge$PLI_x130 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x130, 0)
regen_wedge$NonCon_total <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$total, 0)
regen_wedge$NonCon_x0 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x0, 0)
regen_wedge$NonCon_x10 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x10, 0)
regen_wedge$NonCon_x30 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x30, 0)
regen_wedge$NonCon_x130 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x130, 0)
regen_wedge$Spruce_total <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$total, 0)
regen_wedge$Spruce_x0 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x0, 0)
regen_wedge$Spruce_x10 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x10, 0)
regen_wedge$Spruce_x30 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x30, 0)
regen_wedge$Spruce_x130 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x130, 0)


# remove NR rows for plots that have other species present
regen_wedge <- regen_wedge %>% 
  group_by(Card) %>% 
  mutate(has_nr = any(Species == "NR"), num_rows = n()) %>% 
  filter(num_rows == 1 | !(has_nr & Species == "NR")) %>% 
  select(-has_nr, -num_rows) %>% 
  select(-Plot_Sp)

#regen_wedge <- regen_wedge %>% 
  rename("total_x0" = "x0",
         "total_x10" = "x10",
         "total_x30" = "x30",
         "total_x130" = "x130",
         "total_count" = "total")




regen_wedge1 <- regen_wedge %>% 
  group_by(Card, Quandrant) %>% 
  summarize(SpeciesAll = paste(Species, collapse = ", "),
            total_count = sum(total),
            total_tph = total_count*200,
            total_x0 = sum(x0),
            total_x10 = sum(x10),
            total_x30 = sum(x30),
            total_x130 = sum(x130),
            FDI_count = sum(FDI_total),
            FDI_tph = FDI_count*200,
            FDI_x0 = sum(FDI_x0),
            FDI_x10 = sum(FDI_x10),
            FDI_x30 = sum(FDI_x30),
            FDI_x130 = sum(FDI_x130),
            PLI_count = sum(PLI_total),
            PLI_tph = PLI_count*200,
            PLI_x0 = sum(PLI_x0),
            PLI_x10 = sum(PLI_x10),
            PLI_x30 = sum(PLI_x30),
            PLI_x130 = sum(PLI_x130),
            NonCon_count = sum(NonCon_total),
            NonCon_x0 = sum(NonCon_x0),
            NonCon_x10 = sum(NonCon_x10),
            NonCon_x30 = sum(NonCon_x30),
            NonCon_x130 = sum(NonCon_x130),
            Spruce_count = sum(Spruce_total),
            Spruce_x0 = sum(Spruce_x0),
            Spruce_x10 = sum(Spruce_x10),
            Spruce_x30 = sum(Spruce_x30),
            Spruce_x130 = sum(Spruce_x130)) %>% 
  ungroup()



test <- regen_wedge1 %>% 
  group_by(Card) %>% 
  summarize(total_sd = sqrt(sum((total_count-sum(total_count)/4)^2)/3),
            PLI_sd = sqrt(sum((PLI_count-sum(PLI_count)/4)^2)/3),
            FDI_sd = sqrt(sum((FDI_count-sum(FDI_count)/4)^2)/3))

options(scipen=999)

test <- test %>%
  gather(key = "Species", value = "SD", total_sd, PLI_sd, FDI_sd)

ggplot(data=test, aes(x = SD, fill = Species)) +
  geom_histogram(position = "dodge", bins = 30, color = "white", alpha = 0.7) +
  facet_wrap(~Species) +
  theme_minimal() +
  labs(x="SD (Seedlings per plot)", y="Frequency", title="In Plot Variability") +
  scale_fill_discrete()

ggplot(data=filter(test, SD > 0), aes(x = SD, fill = Species)) +
  geom_histogram(position = "dodge", bins = 30, color = "white", alpha = 0.7) +
  facet_wrap(~Species) +
  theme_minimal() +
  labs(x="SD (Seedlings per plot)", y="Frequency", title="In Plot Variability") +
  scale_fill_discrete()

options(scipen=0)

```

# Dealing with Aspect
```{r}
#northeast-to-southwest facing scale (Beers et al., 1996)
#Taspect = sin(aspect + 45) + 1

##this should be moved
regen_GIS$Con_count <- regen_GIS$FDI_count + regen_GIS$PLI_count + regen_GIS$Spruce_count
regen_GIS$Con_tph <- regen_GIS$Con_count*200
##

asp <- regen_GIS 
asp$aspect <- sin(regen_GIS$Aspect + 45) + 1


#Convert Aspect
assign_direction <- function(angle) {
  ifelse(is.na(angle), NA,  # Handle NA values
         ifelse(angle >= 315 || angle < 45, "N",
                ifelse(angle >= 45 && angle < 135, "E",
                       ifelse(angle >= 135 && angle < 225, "S", "W"))))
  }


# Apply the function to the data column
regen_GIS$Aspect_cat <- sapply(regen_GIS$Aspect, assign_direction)


ggplot(regen_GIS, aes(x=Aspect_cat,y=total_count)) +
  geom_boxplot()

```

# Binary Counts
did it two ways
```{r}
regen_binary <- regen_GIS %>% 
  mutate(total_count_bin = ifelse(total_count>0,1,0),
         total_x0_bin = ifelse(total_x0>0,1,0),
         total_x10_bin = ifelse(total_x10>0,1,0),
         total_x30_bin = ifelse(total_x30>0,1,0),
         total_x130_bin = ifelse(total_x130>0,1,0),
         FDI_count_bin = ifelse(FDI_count>0,1,0),
         FDI_x0_bin = ifelse(FDI_x0>0,1,0),
         FDI_x10_bin = ifelse(FDI_x10>0,1,0),
         FDI_x30_bin = ifelse(FDI_x30>0,1,0),
         FDI_x130_bin = ifelse(FDI_x130>0,1,0),
         PLI_count_bin = ifelse(PLI_count>0,1,0),
         PLI_x0_bin = ifelse(PLI_x0>0,1,0),
         PLI_x10_bin = ifelse(PLI_x10>0,1,0),
         PLI_x30_bin = ifelse(PLI_x30>0,1,0),
         PLI_x130_bin = ifelse(PLI_x130>0,1,0),
         NonCon_count_bin = ifelse(NonCon_count>0,1,0),
         NonCon_x0_bin = ifelse(NonCon_x0>0,1,0),
         NonCon_x10_bin = ifelse(NonCon_x10>0,1,0),
         NonCon_x30_bin = ifelse(NonCon_x30>0,1,0),
         NonCon_x130_bin = ifelse(NonCon_x130>0,1,0),
         Spruce_count_bin = ifelse(Spruce_count>0,1,0),
         Spruce_x0_bin = ifelse(Spruce_x0>0,1,0),
         Spruce_x10_bin = ifelse(Spruce_x10>0,1,0),
         Spruce_x30_bin = ifelse(Spruce_x30>0,1,0),
         Spruce_x130_bin = ifelse(Spruce_x130>0,1,0))

create_binary_columns <- function(data) {
  binary_cols <- c("total_count", "total_x0", "total_x10", "total_x30", "total_x130",
                   "FDI_count", "FDI_x0", "FDI_x10", "FDI_x30", "FDI_x130",
                   "PLI_count", "PLI_x0", "PLI_x10", "PLI_x30", "PLI_x130",
                   "NonCon_count", "NonCon_x0", "NonCon_x10", "NonCon_x30", "NonCon_x130",
                   "Spruce_count", "Spruce_x0", "Spruce_x10", "Spruce_x30", "Spruce_x130")
  
  for (col in binary_cols) {
    binary_col <- paste0(col, "_bin")
    data[[binary_col]] <- ifelse(data[[col]] > 0, 1, 0)
  }
  
  return(data)
}

regen_binary1 <- create_binary_columns(regen_GIS) %>% 
  select(Card, total_count_bin:Spruce_x130_bin)


regen_binary <- regen_binary %>% 
  select(Card, total_count_bin:Spruce_x130_bin)

library(testthat)
test_that("Test if data frames are same", {
  expect_equal(regen_binary,regen_binary1)
})

#combing binary with GIS data
bin_GIS <- left_join(regen_binary,GIS, by = "Card") %>% 
  ungroup()

assign_direction <- function(angle) {
  ifelse(is.na(angle), NA,  # Handle NA values
         ifelse(angle >= 315 || angle < 45, "N",
                ifelse(angle >= 45 && angle < 135, "E",
                       ifelse(angle >= 135 && angle < 225, "S", "W"))))
  }


# Apply the function to the data column
bin_GIS$Aspect_cat <- sapply(bin_GIS$Aspect, assign_direction)
```
#Some graphs with binary
```{r}
#Making graphs
##aspect and total count (no real change IMO)
aspect_graph <- bin_GIS %>%
  group_by(Aspect_cat, total_count_bin) %>%
  summarise(count = n()) 

aspect_graph <- aspect_graph %>%
  group_by(Aspect_cat) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$total_count_bin <- as.factor(aspect_graph$total_count_bin)  

ggplot(filter(aspect_graph, !is.na(Aspect_cat)), aes(x = Aspect_cat, y = percentage, fill = total_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "Total Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and Total Count Bin") +
  theme_minimal() 
 
ggplot(filter(aspect_graph, !is.na(Aspect_cat)), aes(x = Aspect_cat, y = count, fill = total_count_bin)) +
  geom_col(position="dodge") +  # Adjust dodge width as needed # Adjust colors as needed
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "Total Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Count", 
       title = "Count of Observations by Aspect Category and Total Count Bin") +
  theme_minimal() 

#PLI abd aspect
aspect_graph <- bin_GIS %>%
  group_by(Aspect_cat, PLI_count_bin) %>%
  summarise(count = n()) 


aspect_graph <- aspect_graph %>%
  group_by(Aspect_cat) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$PLI_count_bin <- as.factor(aspect_graph$PLI_count_bin)  

ggplot(filter(aspect_graph, !is.na(Aspect_cat)), aes(x = Aspect_cat, y = percentage, fill = PLI_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "PLI Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and PLI Count Bin") +
  theme_minimal() 

#FDI and aspect
aspect_graph <- bin_GIS %>%
  group_by(Aspect_cat, FDI_count_bin) %>%
  summarise(count = n()) 


aspect_graph <- aspect_graph %>%
  group_by(Aspect_cat) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$FDI_count_bin <- as.factor(aspect_graph$FDI_count_bin)  

ggplot(filter(aspect_graph, !is.na(Aspect_cat)), aes(x = Aspect_cat, y = percentage, fill = FDI_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "FDI Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and FDI Count Bin") +
  theme_minimal() 

#NonCon and aspect
aspect_graph <- bin_GIS %>%
  group_by(Aspect_cat, NonCon_count_bin) %>%
  summarise(count = n()) 


aspect_graph <- aspect_graph %>%
  group_by(Aspect_cat) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$NonCon_count_bin <- as.factor(aspect_graph$NonCon_count_bin)  

ggplot(filter(aspect_graph, !is.na(Aspect_cat)), aes(x = Aspect_cat, y = percentage, fill = NonCon_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "NonCon Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and NonCon Count Bin") +
  theme_minimal() 



#next lets try getting them all on the same plot
```

# Occurrence as binary plot

```{r}

names(regen_binary)
regen_for_table <- regen_binary %>% 
  summarise(total_no_occurrence = n()-sum(total_count_bin),
            x0_no_occurrence = n()-sum(total_x0_bin),
            x10_no_occurrence = n()-sum(total_x10_bin),
            x30_no_occurrence = n()-sum(total_x30_bin),
            x130_no_occurrence = n()-sum(total_x130_bin),
            FDI_count_occurrence = sum(FDI_count_bin),
            FDI_x0_occurrence = sum(FDI_x0_bin),
            FDI_x10_occurrence = sum(FDI_x10_bin),
            FDI_x30_occurrence = sum(FDI_x30_bin),
            FDI_x130_occurrence = sum(FDI_x130_bin),
            PLI_count_occurrence = sum(PLI_count_bin),
            PLI_x0_occurrence = sum(PLI_x0_bin),
            PLI_x10_occurrence = sum(PLI_x10_bin),
            PLI_x30_occurrence = sum(PLI_x30_bin),
            PLI_x130_occurrence = sum(PLI_x130_bin),
            NonCon_count_occurrence = sum(NonCon_count_bin),
            NonCon_x0_occurrence = sum(NonCon_x0_bin),
            NonCon_x10_occurrence = sum(NonCon_x10_bin),
            NonCon_x30_occurrence = sum(NonCon_x30_bin),
            NonCon_x130_occurrence = sum(NonCon_x130_bin),
            Spruce_count_occurrence = sum(Spruce_count_bin),
            Spruce_x0_occurrence = sum(Spruce_x0_bin),
            Spruce_x10_occurrence = sum(Spruce_x10_bin),
            Spruce_x30_occurrence = sum(Spruce_x30_bin),
            Spruce_x130_occurrence = sum(Spruce_x130_bin)
            )

regen_table <- gather(regen_for_table, "AgeClass", "Count",1:25)
regen_table$Species <- c("No Regen","No Regen","No Regen","No Regen","No Regen","FDI","FDI",
                         "FDI","FDI","FDI","PLI","PLI","PLI","PLI","PLI","Non Conifer",
                         "Non Conifer","Non Conifer","Non Conifer","Non Conifer", 
                         "Spruce","Spruce","Spruce","Spruce", "Spruce")
regen_table$AgeClass <- c("All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130")

class_order <- c("All heights", "x0", "x10", "x30", "x130")
species_order <- c("PLI","FDI","Spruce","Non Conifer","No Regen")
ggplot(regen_table, aes(x = factor(AgeClass, levels = class_order), y = Count)) +
  geom_col(aes(fill = factor(Species, levels = species_order)), position = "dodge") +
  xlab("Height Class (cm)") +
  ylab("# of Plots with Occurrence") +
  ggtitle("Occurrence of Regen by Height Class and Species") +
  labs(fill = "Species") +
  scale_fill_brewer(palette = "Spectral") +
  scale_x_discrete(labels = c("total" = "All heights", "x0" = "0-9", "x10" = "10-29", "x30" = "30-129", "x130" = "130+")) +
  theme_bw() +
  theme(axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15),
        axis.title.x=element_text(size=20),
        axis.title.y=element_text(size=20),
        plot.title = element_text(size = 20),
        legend.text = element_text(size=15),
        legend.title = element_text(size=20))
```


