---
title: "Overstory"
author: "Nat"
date: "2024-03-12"
output: html_document
---

```{r}
library(tidyverse)

overstory_1 <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Overstory.csv"
overstory_1 <- read.csv(overstory_1)
regen <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Regen_2023_ALL.csv" ##check this
regen <- read.csv(regen)
site <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Site.csv"
site <- read.csv(site)
GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/GIS_fixed.csv"
GIS <- read.csv(GIS)
internal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Internal.csv" ##check this
internal <- read.csv(internal)
basal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/BasalArea.csv"
basal <- read.csv(basal)
regen_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_GIS.csv"
regen_GIS <- read.csv(regen_GIS)
bin_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/binary_GIS.csv"
bin_GIS <- read.csv(bin_GIS)
regen_binary <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_binary.csv"
regen_binary <- read.csv(regen_binary)
measured_plots <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/MeasuredPlots.csv"
measured_plots <- read.csv(measured_plots)
```

```{r}
overstory_1$Species <- sub("AT", "NonCon", overstory_1$Species)
overstory_1$Species <- sub("SW", "Spruce", overstory_1$Species)
overstory_1$Species <- sub("SE", "Spruce", overstory_1$Species)
overstory_1$Species <- sub("SX", "Spruce", overstory_1$Species)
```

Now I need to delete all the blank rows. For now, I'm going to leave a blank row if the plot has no overstory
```{r}
site <- site %>% 
  dplyr::select(Card, Notes)
site$Card <- as.integer(site$Card)
overstory_1$Card <- as.integer(overstory_1$Card)

overstory <- overstory_1 %>% 
  group_by(Card) %>% 
  filter(!is.na(TreeNumber)) %>% 
  dplyr::select(Card, TreeNumber:Notes)

overstory <- full_join(overstory, site, by = "Card")
overstory$DBH[is.na(overstory$DBH)] <- 0


```

Okay now I need to start doing something with this data. 
Going to make some summaries by plot. 
```{r}
overstory %>% 
  group_by(Card) %>% 
  filter(is.na(Status)) %>% 
  summarise(n())
  
```
Trees
-seed trees
-shade!
-size of trees (basal area)
-density (size classes, live and dead, basal area)
-is there salvage logging?
-tables/graphs by fire severity class
```{r}
#add basal area column


overstory$Basal <- pi*(overstory$DBH/200)^2
BasalArea <- overstory %>% 
  group_by(Card) %>% 
  summarise(LiveBasal = sum(Basal[Status == "L"])/.01,
            DeadBasal = sum(Basal[Status == "D"])/.01,
            TotalBasal = sum(Basal)/.01,
            LiveBasal_PLI = sum(Basal[Status == "L" & Species == "PLI"])/.01,
            DeadBasal_PLI = sum(Basal[Status == "D" & Species == "PLI"])/.01,
            TotalBasal_PLI = sum(Basal[Species == "PLI"])/.01,
            LiveBasal_FDI = sum(Basal[Status == "L" & Species == "FDI"])/.01,
            DeadBasal_FDI = sum(Basal[Status == "D" & Species == "FDI"])/.01,
            TotalBasal_FDI = sum(Basal[Species == "FDI"])/.01,
            LiveBasal_Spruce = sum(Basal[Status == "L" & Species == "Spruce"])/.01,
            DeadBasal_Spruce = sum(Basal[Status == "D" & Species == "Spruce"])/.01,
            TotalBasal_Spruce = sum(Basal[Species == "Spruce"])/.01,
            LiveBasal_NonCon = sum(Basal[Status == "L" & Species == "NonCon"])/.01,
            DeadBasal_NonCon = sum(Basal[Status == "D" & Species == "NonCon"])/.01,
            TotalBasal_NonCon = sum(Basal[Species == "NonCon"])/.01)

BasalArea <- BasalArea %>%
  filter(!is.na(Card)) %>% 
  replace(is.na(.),0)

#write.csv(BasalArea, "C:/Users/nmac2000/Documents/regen project/Regen/Dataframes/BasalArea.csv", row.names = FALSE)

```

basal area and GIS data
```{r}
basal_GIS <- full_join(BasalArea, GIS, by="Card")
#write.csv(basal_GIS, "C:/Users/nmac2000/Documents/regen project/Regen/Dataframes/BasalGIS.csv", row.names = FALSE)
```
basal area compared to different variables
```{r}
ggplot(basal_GIS, aes(x=Fire_Severity_1, y=DeadBasal)) +
  geom_boxplot()

ggplot(basal_GIS, aes(x=Fire_Severity_1, y=LiveBasal)) +
  geom_boxplot()

ggplot(basal_GIS, aes(x= Fire_Severity_1)) +
  geom_boxplot(aes(y=DeadBasal), color="blue", width = .4) +
  geom_boxplot(aes(y=LiveBasal), color="red", position = position_nudge(x= 0.3), width = .4) 


```


I want to look at the notes for each plot and see if there plots that should be removed because they weren't actually sampled
```{r}

site_notes <- site %>% 
  dplyr::select(Card, Notes) %>% 
  filter(str_length(Notes) >1)

#write.csv(site_notes, "C:/Users/nmac2000/Documents/regen project/Data/SiteNotes.csv", row.names = FALSE)

not_sampled_check <- left_join(site_notes, measured_plots, by = "Card")
not_sampled <- not_sampled_check %>% 
  filter(total_count == 0)
#what is the X variable?

#okay this is a good start. It seems like most of these on this list were not actually sampled. There are a few I should double check
```
#Look at how many trees of each species are at each plot
and then compare it to VRI layer and regen composition
```{r}
#for all trees
plot_comp <- overstory %>% 
  group_by(Card, Species) %>%
  replace_na(list(DBH = 0, Height = 0)) %>% 
  summarise(Count = n(),
            AvgHt = mean(Height, na.rm = T),
            AvgDBH = mean(DBH, na.rm = T),
            MaxHt = max(Height, na.rm = T),
            MaxDBH = max(DBH, na.rm = T)) 

overstory_metrics <- plot_comp %>% 
  group_by(Card) %>% 
  summarize(Highest_avg_dbh = Species[which.max(AvgDBH)],
            Highest_avg_ht = Species[which.max(AvgHt)],
            Max_count = Species[which.max(Count)],
            Max_dbh = Species[which.max(MaxDBH)],
            Max_ht = Species[which.max(MaxHt)])

overstory_metrics <- full_join(overstory_metrics, regen_GIS)
overstory_metrics <- overstory_metrics %>% 
  dplyr::select(Card:Max_ht, Species_1, SpeciesAll, total_count:Spruce_x130)

#for dead trees
plot_comp_dead <- overstory %>% 
  group_by(Card, Species) %>%
  replace_na(list(DBH = 0, Height = 0)) %>% 
  filter(Status == "D") %>% 
  summarise(Count = n(),
            AvgHt = mean(Height, na.rm = T),
            AvgDBH = mean(DBH, na.rm = T),
            MaxHt = max(Height, na.rm = T),
            MaxDBH = max(DBH, na.rm = T)) 

overstory_metrics_dead <- plot_comp_dead %>% 
  group_by(Card) %>% 
  summarize(Highest_avg_dbh = Species[which.max(AvgDBH)],
            Highest_avg_ht = Species[which.max(AvgHt)],
            Max_count = Species[which.max(Count)],
            Max_dbh = Species[which.max(MaxDBH)],
            Max_ht = Species[which.max(MaxHt)])

overstory_metrics_dead <- full_join(overstory_metrics_dead, regen_GIS)
overstory_metrics_dead <- overstory_metrics_dead %>% 
  dplyr::select(Card:Max_ht, Species_1, SpeciesAll, total_count:Spruce_x130)

#for live trees
plot_comp_live <- overstory %>% 
  group_by(Card, Species) %>%
  replace_na(list(DBH = 0, Height = 0)) %>% 
  filter(Status == "L") %>% 
  summarise(Count = n(),
            AvgHt = mean(Height, na.rm = T),
            AvgDBH = mean(DBH, na.rm = T),
            MaxHt = max(Height, na.rm = T),
            MaxDBH = max(DBH, na.rm = T)) 

overstory_metrics_live <- plot_comp_live %>% 
  group_by(Card) %>% 
  summarize(Highest_avg_dbh = Species[which.max(AvgDBH)],
            Highest_avg_ht = Species[which.max(AvgHt)],
            Max_count = Species[which.max(Count)],
            Max_dbh = Species[which.max(MaxDBH)],
            Max_ht = Species[which.max(MaxHt)])

overstory_metrics_live <- full_join(overstory_metrics_live, regen_GIS)
overstory_metrics_live <- overstory_metrics_live %>% 
  dplyr::select(Card:Max_ht, Species_1, SpeciesAll, total_count:Spruce_x130)

ggplot(overstory_metrics, aes(x=Max_count)) +
  geom_bar(aes(fill = Max_count)) +
  facet_wrap(~Species_1)

ggplot(filter(filter(overstory_metrics, Species_1 == "PLI"), FDI_count < 1000)) +
  geom_histogram(aes(x=FDI_count), fill= "lightgreen", binwidth = 10, position="dodge") +
  geom_histogram(aes(x=PLI_count), fill="darkgreen", binwidth = 10, position="dodge")

# Check the column names in your dataset
colnames(overstory_metrics)


filtered_data <- overstory_metrics %>%
  filter(Species_1 == "PLI", FDI_count < 1000, PLI_count < 1000) %>%
  dplyr::select(FDI_count, PLI_count)

# Reshape data to long format
tidy_data <- filtered_data %>%
  pivot_longer(cols = c(FDI_count, PLI_count), names_to = "Variable", values_to = "Count")

ggplot(tidy_data, aes(x = Count, fill = Variable)) +
  geom_histogram(binwidth = 50, position = "stack") +
  scale_fill_manual(values = c("FDI_count" = "lightgreen", "PLI_count" = "darkgreen")) +
  labs(x = "Count") +
  theme_minimal()
```

```{r}
regen_GIS %>% 
  filter(Species_1 == "", Harvest_Date_1=="") %>% 
  dplyr::select(Card,Species_1, Fire_Year_1, Harvest_Date_1) 
```

```{r}
#looking at seedlings and pre-fire overstory

regen_GIS %>% 
  filter(Species_1 == "Spruce",
         total_count > 0,
         Spruce_count == 0) 

regen_GIS %>% 
  filter(SpeciesAll %in% "NR",
         total_count > 0)

regen_GIS %>% 
  filter(Species_1 == "FDI",
         FDI_count < PLI_count) %>% 
  dplyr::select(SpeciesAll, total_count, FDI_count, PLI_count)

```






```{r}
regen_GIS %>% 
  filter
```
