---
title: "Climate"
author: "Nat"
date: "2024-04-25"
output: html_document
---
# Load dataframes and packages

```{r}
library(tidyverse)
library(ClimateNAr)
library(sf)

regen <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Regen_2023_ALL.csv"
regen <- read.csv(regen)
site <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Site.csv"
site <- read.csv(site)
GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/GIS_fixed.csv"
GIS <- read.csv(GIS)
internal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Internal.csv"
internal <- read.csv(internal)
basal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/BasalArea.csv"
basal <- read.csv(basal)
regen_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_GIS.csv"
regen_GIS <- read.csv(regen_GIS)
bin_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/binary_GIS.csv"
bin_GIS <- read.csv(bin_GIS)
regen_binary <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_binary.csv"
regen_binary <- read.csv(regen_binary)
actual_coords <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Plot_coordinates_actual.csv"
actual_coords <- read.csv(actual_coords)

```
#Get coords for actual plots
```{r}
#need to convert utm to lat/long

utm_crs <- "+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs"
# Create an sf object
utm_sf <- st_as_sf(actual_coords, coords = c("Easting", "Northing"), crs = utm_crs)

st_crs(utm_sf)

# Convert to latitude/longitude
lat_lon_sf <- st_transform(utm_sf, crs = st_crs("+proj=longlat +datum=WGS84"))
lat_lon_sf <- st_set_precision(lat_lon_sf, 10)

# Extract coordinates and bind to original data
lat_lon_coords <- round(st_coordinates(lat_lon_sf), digits = 10)
lat_lon_data <- cbind(actual_coords, lat_lon_coords)

lat_lon_data <- lat_lon_data %>% 
  rename(#lat = "Y",
         #long = "X",
         SampleSite_ID = "Card")
#write.csv(lat_lon_data, "C:/Users/nmac2000/Documents/regen project/Data/UTM_Lat_Lon.csv")
lat_lon_data <- read.csv("C:/Users/nmac2000/Documents/regen project/Data/UTM_Lat_Lon.csv")
```


#Now need to break up by fire year
```{r}
forClim1 <- regen_GIS %>% 
  dplyr::select(SampleSite_ID, Elevation, FIRE_YEAR_1)

forClim1<- full_join(forClim1, lat_lon_data, by="SampleSite_ID")

forClim1 <- forClim1 %>% 
  rename(PlotID = `SampleSite_ID`) %>% 
  dplyr::select(PlotID, FIRE_YEAR_1, lat, long, Elevation) %>% 
  rename(ID1 = "PlotID",
         ID2 = "FIRE_YEAR_1",
         el = "Elevation")

table(forClim1$ID2)

forClim2003 <- forClim1 %>% 
  dplyr::filter(ID2== 2003)
#write.csv(forClim2003, "C:/Users/nmac2000/Documents/regen project/Data/ClimateBC/plots2003.csv")

forClim2009 <- forClim1 %>% 
  filter(ID2== 2009)
#write.csv(forClim2009, "C:/Users/nmac2000/Documents/regen project/Data/ClimateBC/plots2009.csv")

forClim2010 <- forClim1 %>% 
  filter(ID2== 2010)

forClim2015 <- forClim1 %>% 
  filter(ID2== 2015)

forClim2016 <- forClim1 %>% 
  filter(ID2== 2016)

forClim2017 <- forClim1 %>% 
  filter(ID2== 2017)

forClim2023 <- forClim1 %>% 
  filter(ID2== 2023)

## need to break 2017 into multiple data frame for Climate NA
```


```{r}
#clim2003.2004 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2004.ann', MSY='SY')
#clim2003.2005 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2005.ann', MSY='SY')
#clim2003.2006 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2006.ann', MSY='SY')
#clim2003.2007 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2007.ann', MSY='SY')
#clim2003.2008 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2008.ann', MSY='SY')
#write.csv(clim2003.2004, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/2004.csv")
clim2003.2004 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2003/2004.csv")
#write.csv(clim2003.2005, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/2005.csv")
clim2003.2005 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2003/2005.csv")
#write.csv(clim2003.2006, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/2006.csv")
clim2003.2006 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2003/2006.csv")

#clim2003.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2003.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/normal.csv")

#clim2009.2010 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2010.ann', MSY='SY')
#clim2009.2011 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2011.ann', MSY='SY')
#clim2009.2012 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2012.ann', MSY='SY')
#clim2009.2013 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2013.ann', MSY='SY')
#clim2009.2014 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2014.ann', MSY='SY')
#write.csv(clim2009.2010, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2010.csv")
clim2009.2010 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2010.csv")
#write.csv(clim2009.2011, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2011.csv")
clim2009.2011 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2011.csv")
#write.csv(clim2009.2012, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2012.csv")
clim2009.2012 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2012.csv")
#write.csv(clim2009.2013, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2013.csv")
clim2009.2013 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2013.csv")
#write.csv(clim2009.2014, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2014.csv")
clim2009.2014 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2014.csv")

#clim2009.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2009.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/normal.csv")
clim2009.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/normal.csv")

#clim2010.2011 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2011.ann', MSY='SY')
#clim2010.2012 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2012.ann', MSY='SY')
#clim2010.2013 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2013.ann', MSY='SY')
#clim2010.2014 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2014.ann', MSY='SY')
#clim2010.2015 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2015.ann', MSY='SY')
#write.csv(clim2010.2011, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2011.csv")
clim2010.2011 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2011.csv")
#write.csv(clim2010.2012, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2012.csv")
clim2010.2012 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2012.csv")
#write.csv(clim2010.2013, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2013.csv")
clim2010.2013 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2013.csv")
#write.csv(clim2010.2012, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2014.csv")
clim2010.2014 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2014.csv")
#write.csv(clim2010.2013, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2015.csv")
clim2010.2015 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2015.csv")

#clim2010.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2010.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/normal.csv")
clim2010.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/normal.csv")

#clim2015.2016 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2016.ann', MSY='SY')
#clim2015.2017 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2017.ann', MSY='SY')
#clim2015.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2018.ann', MSY='SY')
#clim2015.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2019.ann', MSY='SY')
#clim2015.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2020.ann', MSY='SY')
#write.csv(clim2015.2016, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2016.csv")
clim2015.2016 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2016.csv")
#write.csv(clim2015.2017, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2017.csv")
clim2015.2017 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2017.csv")
#write.csv(clim2015.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2018.csv")
clim2015.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2018.csv")
#write.csv(clim2015.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2019.csv")
clim2015.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2019.csv")
#write.csv(clim2015.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2020.csv")
clim2015.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2020.csv")

#clim2015.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2015.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/normal.csv")
clim2015.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/normal.csv")

###

#clim2016.2017 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2017.ann', MSY='SY')
#clim2016.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2018.ann', MSY='SY')
#clim2016.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2019.ann', MSY='SY')
#clim2016.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2020.ann', MSY='SY')
#clim2016.2021 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2021.ann', MSY='SY')
#write.csv(clim2016.2017, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2017.csv")
clim2016.2017 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2017.csv")
#write.csv(clim2016.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2018.csv")
clim2016.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2018.csv")
#write.csv(clim2016.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2019.csv")
clim2016.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2019.csv")
#write.csv(clim2016.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2020.csv")
clim2016.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2020.csv")
#write.csv(clim2016.2021, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2021.csv")
clim2016.2021 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2021.csv")

#clim2016.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2016.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/normal.csv")
clim2016.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/normal.csv")


###2017 data needs to be split up
forClim2017a <- forClim2017[1:100,]
forClim2017b <- forClim2017[101:200,]
forClim2017c <- forClim2017[201:288,]

#clim2017a.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2018.ann', MSY='SY')
#clim2017a.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2019.ann', MSY='SY')
#clim2017a.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2020.ann', MSY='SY')
#clim2017a.2021 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2021.ann', MSY='SY')
#clim2017a.2022 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2022.ann', MSY='SY')
#write.csv(clim2017a.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2018a.csv")
clim2017a.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2018a.csv")
#write.csv(clim2017a.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2019a.csv")
clim2017a.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2019a.csv")
#write.csv(clim2017a.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2020a.csv")
clim2017a.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2020a.csv")
#write.csv(clim2017a.2021, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2021a.csv")
clim2017a.2021 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2021a.csv")
#write.csv(clim2017a.2022, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2022a.csv")
clim2017a.2022 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2022a.csv")

#clim2017a.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2017a.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/normala.csv")
clim2017a.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/normala.csv")

#clim2017b.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2018.ann', MSY='SY')
#clim2017b.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2019.ann', MSY='SY')
#clim2017b.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2020.ann', MSY='SY')
#clim2017b.2021 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2021.ann', MSY='SY')
#clim2017b.2022 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2022.ann', MSY='SY')
#write.csv(clim2017b.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2018b.csv")
clim2017b.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2018b.csv")
#write.csv(clim2017b.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2019b.csv")
clim2017b.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2019b.csv")
#write.csv(clim2017b.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2020b.csv")
clim2017b.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2020b.csv")
#write.csv(clim2017b.2021, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2021b.csv")
clim2017b.2021 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2021b.csv")
#write.csv(clim2017b.2022, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2022b.csv")
clim2017b.2022 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2022b.csv")

#clim2017b.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2017b.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/normalb.csv")
clim2017b.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/normalb.csv")

#clim2017c.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2018.ann', MSY='SY')
#clim2017c.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2019.ann', MSY='SY')
#clim2017c.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2020.ann', MSY='SY')
#clim2017c.2021 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2021.ann', MSY='SY')
#clim2017c.2022 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2022.ann', MSY='SY')
#write.csv(clim2017c.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2018c.csv")
clim2017c.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2018c.csv")
#write.csv(clim2017c.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2019c.csv")
clim2017c.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2019c.csv")
#write.csv(clim2017c.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2020c.csv")
clim2017c.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2020c.csv")
#write.csv(clim2017c.2021, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2021c.csv")
clim2017c.2021 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2021c.csv")
#write.csv(clim2017c.2022, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2022c.csv")
clim2017c.2022 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2022c.csv")

#clim2017c.normal <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Normal_1981_2010.nrm', MSY='SY')
#write.csv(clim2017c.normal, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/normalc.csv")
clim2017c.normal <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/normalc.csv")
```
# Filter out plots
```{r}
clim2009.2010 <- clim2009.2010 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2009.2011 <- clim2009.2011 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2009.2012 <- clim2009.2012 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2009.2013 <- clim2009.2013 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2009.2014 <- clim2009.2014 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2009.normal <- clim2009.normal %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2010.2011 <- clim2010.2011 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2010.2012 <- clim2010.2012 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2010.2013 <- clim2010.2013 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2010.2014 <- clim2010.2014 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2010.2015 <- clim2010.2015 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2010.normal <- clim2010.normal %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2015.2016 <- clim2015.2016 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2015.2017 <- clim2015.2017 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2015.2018 <- clim2015.2018 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2015.2019 <- clim2015.2019 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2015.2020 <- clim2015.2020 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2015.normal <- clim2015.normal %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2016.2017 <- clim2016.2017 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2016.2018 <- clim2016.2018 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2016.2019 <- clim2016.2019 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2016.2020 <- clim2016.2020 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2016.2021 <- clim2016.2021 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2016.normal <- clim2016.normal %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2017.2018 <- rbind(clim2017a.2018,clim2017b.2018,clim2017c.2018)
clim2017.2018 <- clim2017.2018 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2017.2019 <- rbind(clim2017a.2019,clim2017b.2019,clim2017c.2019)
clim2017.2019 <- clim2017.2019 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2017.2020 <- rbind(clim2017a.2020,clim2017b.2020,clim2017c.2020)
clim2017.2020 <- clim2017.2020 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2017.2021 <- rbind(clim2017a.2021,clim2017b.2021,clim2017c.2021)
clim2017.2021 <- clim2017.2021 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2017.2022 <- rbind(clim2017a.2022,clim2017b.2022,clim2017c.2022)
clim2017.2022 <- clim2017.2022 %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)

clim2017.normal <- rbind(clim2017a.normal,clim2017b.normal,clim2017c.normal)
clim2017.normal <- clim2017.normal %>% 
  filter(ID1 %in% bin_dis_GIS1$SampleSite_ID) %>% 
  distinct(ID1, .keep_all = T)
```

#need to now make compiled data frame for each year and find mins, maxs, and avgs
variables of interest:
  -MAT mean annual temperature
  -MWMT mean warmest month temperature
  -MCMT mean coldest month temperature
  -NFFD number of frost free days
  -PAS precipitation as snow
  -Eref Hargreaves reference evaporation
  -CMD Hargreaves climatic moisture deficit
  -AHM annual heat-moisture index
  -SHM summer heat-moisture index
  -Tave_sp spring mean temp
  -Tave_sm summer mean temp
  -Tmax_sp spring max temp
  -Tmax_sm summer max temp
  -Tmin_sp spring min temp
  -Tmin_sm summer min temp
  -PPT_wt winter precipitation
  -PPT_sp spring precipitation
  -PPT_sm summer precipitation
  -NFFD_sp spring number of frost free days
  -PAS_wt
  -PAS_sp spring precipitation as snow
  -Eref_sm summer Hargreaves reference evaporation
  -CMD_sm summer Hargreaves climatic moisture deficit
  -CMI_sm Summer Hogg's climate moisture index 
  
  
  
  
```{r}
select(MAT, MWMT, MCMT, NFFD, PAS, Eref, CMD, AHM, SHM, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, 
       Tmin_sp, Tmin_sm, PPT_wt, PPT_sp, PPT_sm, NFFD_sp, PAS_wt, PAS_sp, Eref_sm, CMD_sm, CMI_sm)

```

#Combine different years
#need to add mean coldest month
```{r}
#2017 had 3 different df because it was so large

clim2017.2018$Year <- 1
clim2017.2018 <- subset(clim2017.2018, select = -c(X))

#clim2017a.2019 <- subset(clim2017a.2019, select = -c(X.1))

clim2017.2019$Year <- 2
clim2017.2019 <- subset(clim2017.2019, select = -c(X))


clim2017.2020$Year <- 3
clim2017.2020 <- subset(clim2017.2020, select = -c(X))


clim2017.2021$Year <- 4
clim2017.2021 <- subset(clim2017.2021, select = -c(X))


clim2017.2022$Year <- 5
clim2017.2022 <- subset(clim2017.2022, select = -c(X))


clim2017.normal$Year <- 0
clim2017.normal <- select(clim2017.normal, -X)

clim2017 <- rbind(clim2017.2018, clim2017.2019, clim2017.2020, clim2017.2021, clim2017.2022, clim2017.normal)

#2003
#clim2003.2004$Year <- 1
#clim2003.2005$Year <-2
#clim2003.2006$Year <-3
#clim2003.normal$Year <- 0
#clim2003 <- rbind(clim2003.2004,clim2003.2005,clim2003.2006,clim2003.normal)

#2009
clim2009.2010$Year <- 1
clim2009.2011$Year <-2
clim2009.2012$Year <-3
clim2009.2013$Year <-4
clim2009.2014$Year <-5
clim2009.normal$Year <- 0
clim2009 <- rbind(clim2009.2010, clim2009.2011, clim2009.2012, clim2009.2013, clim2009.2014)
clim2009 <- subset(clim2009, select = -c(X))
clim2009.normal <- select(clim2009.normal, -X)
clim2009 <- rbind(clim2009, clim2009.normal)


#2010
clim2010.2011$Year <- 1
clim2010.2012$Year <-2
clim2010.2013$Year <-3
clim2010.2014$Year <-4
clim2010.2015$Year <-5
clim2010.normal$Year <- 0
clim2010 <- rbind(clim2010.2011,clim2010.2012,clim2010.2013,clim2010.2014,clim2010.2015)
clim2010 <- subset(clim2010, select = -c(X))
clim2010.normal <- select(clim2010.normal, -X)
clim2010 <- rbind(clim2010, clim2010.normal)

#2015
clim2015.2016$Year <- 1
clim2015.2017$Year <-2
clim2015.2018$Year <-3
clim2015.2019$Year <-4
clim2015.2020$Year <-5
clim2015.normal$Year <- 0
clim2015 <- rbind(clim2015.2016,clim2015.2017,clim2015.2018,clim2015.2019,clim2015.2020)
clim2015 <- subset(clim2015, select = -c(X))
clim2015.normal <- select(clim2015.normal, -X)
clim2015 <- rbind(clim2015, clim2015.normal)

#2016
clim2016.2017$Year <- 1
clim2016.2018$Year <-2
clim2016.2019$Year <-3
clim2016.2020$Year <-4
clim2016.2021$Year <-5
clim2016.normal$Year <- 0
clim2016.2018$X <- 1
clim2016 <- rbind(clim2016.2017,clim2016.2018,clim2016.2019,clim2016.2020,clim2016.2021)
clim2016 <- subset(clim2016, select = -c(X))
clim2016.normal <- select(clim2016.normal, -X)
clim2016 <- rbind(clim2016, clim2016.normal)

#All
clim.all <- rbind(clim2009, clim2010, clim2015, clim2016, clim2017)
clim.all <- clim.all %>% 
  select(ID1, ID2, Year, MAT, MWMT, MCMT, MAP, NFFD, PAS, AHM, SHM, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp, PAS_wt, PPT_sm, CMI_sm, MCMT) %>% 
  rename(SampleSite_ID = "ID1")
#write.csv(clim.all, "C:/Users/nmac2000/Documents/regen project/Regen/Dataframes/clim_all.csv")
clim.all <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/refs/heads/main/Dataframes/clim_all.csv") %>% select(-X)
```



#finding z scores
```{r}
PAS_wt.sd <- sd(filter(clim.all, Year == 0)$PAS_wt)
PAS_wt.mean <- mean(filter(clim.all, Year == 0)$PAS_wt)
PAS_wt <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, PAS_wt) %>% 
  mutate(zscore = (PAS_wt-PAS_wt.mean)/PAS_wt.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.PAS_wt = sum(zscore > 2),
            hot.dry.anomalies.PAS_wt = sum (zscore < -2))

PPT_sm.sd <- sd(filter(clim.all, Year == 0)$PPT_sm)
PPT_sm.mean <- mean(filter(clim.all, Year == 0)$PPT_sm)
PPT_sm <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, PPT_sm) %>% 
  mutate(zscore = (PPT_sm-PPT_sm.mean)/PPT_sm.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.PPT_sm = sum(zscore > 2),
            hot.dry.anomalies.PPT_sm = sum (zscore < -2))

PAS_sp.sd <- sd(filter(clim.all, Year == 0)$PAS_sp)
PAS_sp.mean <- mean(filter(clim.all, Year == 0)$PAS_sp)
PAS_sp <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, PAS_sp) %>% 
  mutate(zscore = (PAS_sp-PAS_sp.mean)/PAS_sp.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.PAS_sp = sum(zscore > 2),
            hot.dry.anomalies.PAS_sp = sum (zscore < -2))

NFFD_sp.sd <- sd(filter(clim.all, Year == 0)$NFFD_sp)
NFFD_sp.mean <- mean(filter(clim.all, Year == 0)$NFFD_sp)
NFFD_sp <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, NFFD_sp) %>% 
  mutate(zscore = (NFFD_sp-NFFD_sp.mean)/NFFD_sp.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(pos.anomalies.NFFD_sp = sum(zscore > 2),
            neg.anomalies.NFFD_sp = sum (zscore < -2))

Tmin_sp.sd <- sd(filter(clim.all, Year == 0)$Tmin_sp)
Tmin_sp.mean <- mean(filter(clim.all, Year == 0)$Tmin_sp)
Tmin_sp <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, Tmin_sp) %>% 
  mutate(zscore = (Tmin_sp-Tmin_sp.mean)/Tmin_sp.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.Tmin_sp = sum(zscore > 2),
            cool.wet.anomalies.Tmin_sp = sum (zscore < -2))

Tmin_sm.sd <- sd(filter(clim.all, Year == 0)$Tmin_sm)
Tmin_sm.mean <- mean(filter(clim.all, Year == 0)$Tmin_sm)
Tmin_sm <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, Tmin_sm) %>% 
  mutate(zscore = (Tmin_sm-Tmin_sm.mean)/Tmin_sm.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.Tmin_sm = sum(zscore > 2),
            cool.wet.anomalies.Tmin_sm = sum (zscore < -2))

Tmax_sp.sd <- sd(filter(clim.all, Year == 0)$Tmax_sp)
Tmax_sp.mean <- mean(filter(clim.all, Year == 0)$Tmax_sp)
Tmax_sp <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, Tmax_sp) %>% 
  mutate(zscore = (Tmax_sp-Tmax_sp.mean)/Tmax_sp.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.Tmax_sp = sum(zscore > 2),
            cool.wet.anomalies.Tmax_sp = sum (zscore < -2))

Tmax_sm.sd <- sd(filter(clim.all, Year == 0)$Tmax_sm)
Tmax_sm.mean <- mean(filter(clim.all, Year == 0)$Tmax_sm)
Tmax_sm <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, Tmax_sm) %>% 
  mutate(zscore = (Tmax_sm-Tmax_sm.mean)/Tmax_sm.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.Tmax_sm = sum(zscore > 2),
            cool.wet.anomalies.Tmax_sm = sum (zscore < -2))

Tave_sm.sd <- sd(filter(clim.all, Year == 0)$Tave_sm)
Tave_sm.mean <- mean(filter(clim.all, Year == 0)$Tave_sm)
Tave_sm <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, Tave_sm) %>% 
  mutate(zscore = (Tave_sm-Tave_sm.mean)/Tave_sm.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.Tave_sm = sum(zscore > 2),
            cool.wet.anomalies.Tave_sm = sum (zscore < -2))

Tave_sp.sd <- sd(filter(clim.all, Year == 0)$Tave_sp)
Tave_sp.mean <- mean(filter(clim.all, Year == 0)$Tave_sp)
Tave_sp <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, Tave_sp) %>% 
  mutate(zscore = (Tave_sp-Tave_sp.mean)/Tave_sp.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.Tave_sp = sum(zscore > 2),
            cool.wet.anomalies.Tave_sp = sum (zscore < -2))

SHM.sd <- sd(filter(clim.all, Year == 0)$SHM)
SHM.mean <- mean(filter(clim.all, Year == 0)$SHM)
SHM <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, SHM) %>% 
  mutate(zscore = (SHM-SHM.mean)/SHM.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.SHM = sum(zscore > 2),
            cool.wet.anomalies.SHM = sum (zscore < -2))

AHM.sd <- sd(filter(clim.all, Year == 0)$AHM)
AHM.mean <- mean(filter(clim.all, Year == 0)$AHM)
AHM <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, AHM) %>% 
  mutate(zscore = (AHM-AHM.mean)/AHM.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.AHM = sum(zscore > 2),
            cool.wet.anomalies.AHM = sum (zscore < -2))

MAT.sd <- sd(filter(clim.all, Year == 0)$MAT)
MAT.mean <- mean(filter(clim.all, Year == 0)$MAT)
MAT <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, MAT) %>% 
  mutate(zscore = (MAT-MAT.mean)/MAT.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.MAT = sum(zscore > 2),
            cool.wet.anomalies.MAT = sum (zscore < -2))


MAP.sd <- sd(filter(clim.all, Year == 0)$MAP)
MAP.mean <- mean(filter(clim.all, Year == 0)$MAP)
MAP <- clim.all %>% 
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, MAP) %>% 
  mutate(zscore = (MAP-MAP.mean)/MAP.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.MAP = sum(zscore > 2),
            hot.dry.anomalies.MAP = sum (zscore < -2))

MWMT.sd <- sd(filter(clim.all, Year == 0)$MWMT)
MWMT.mean <- mean(filter(clim.all, Year == 0)$MWMT)
MWMT <- clim.all %>%  
  filter(Year != 0) %>% 
  select(SampleSite_ID, ID2, Year, MWMT) %>% 
  mutate(zscore = (MWMT-MWMT.mean)/MWMT.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(hot.dry.anomalies.MWMT = sum(zscore > 2),
            cool.wet.anomalies.MWMT = sum (zscore < -2))

PAS.sd <- sd(filter(clim.all, Year == 0)$PAS)
PAS.mean <- mean(filter(clim.all, Year == 0)$PAS)
PAS <- clim.all %>%  
  filter(Year != 0) %>%
  select(SampleSite_ID, ID2, Year, PAS) %>% 
  mutate(zscore = (PAS-PAS.mean)/PAS.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.PAS = sum(zscore > 2),
            hot.dry.anomalies.PAS = sum (zscore < -2))

MCMT.sd <- sd(filter(clim.all, Year == 0)$MCMT)
MCMT.mean <- mean(filter(clim.all, Year == 0)$MCMT)
MCMT <- clim.all %>%  
  filter(Year != 0) %>%
  select(SampleSite_ID, ID2, Year, MCMT) %>% 
  mutate(zscore = (MCMT-MCMT.mean)/MCMT.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.MCMT = sum(zscore > 2),
            hot.dry.anomalies.MCMT = sum (zscore < -2))

CMI_sm.sd <- sd(filter(clim.all, Year == 0)$CMI_sm)
CMI_sm.mean <- mean(filter(clim.all, Year == 0)$CMI_sm)
CMI_sm <- clim.all %>%  
  filter(Year != 0) %>%
  select(SampleSite_ID, ID2, Year, CMI_sm) %>% 
  mutate(zscore = (CMI_sm-CMI_sm.mean)/CMI_sm.sd) %>% 
  group_by(SampleSite_ID) %>% 
  summarize(cool.wet.anomalies.CMI_sm = sum(zscore > 2),
            hot.dry.anomalies.CMI_sm = sum (zscore < -2))


data_frames <- list(MAT, MWMT, MAP, PAS, AHM, SHM, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp, PAS_wt, PPT_sm, CMI_sm, MCMT)
zscores <- Reduce(function(x, y) merge(x, y, by = "SampleSite_ID"), data_frames)
bin_dis_GIS <- bin_dis_GIS1 %>% 
  select(SampleSite_ID, PLI_count_bin, FDI_count_bin, FIRE_YEAR_1) %>% 
  rename(ID2 = "FIRE_YEAR_1")
#zscores <- rename(zscores, SampleSite_ID = "ID1")
zscores.regen <- left_join(zscores, bin_dis_GIS, by="SampleSite_ID")

zscore.sums <- zscores %>%
  group_by(SampleSite_ID) %>%
  summarize(hot.dry.sum = sum(across(starts_with("hot.dry"))),
            cool.wet.sum = sum(across(starts_with("cool.wet"))))

zscore.sums$SampleSite_ID <- as.numeric(zscore.sums$SampleSite_ID)
zscores.regen <- left_join(zscore.sums, bin_dis_GIS1, by= "SampleSite_ID") 
# zscores.regen <- select(zscores.regen, SampleSite_ID, hot.dry.sum, cool.wet.sum, PLI_count_bin, FDI_count_bin)

```
# Max and Mean and Min
```{r}
mmm <- clim.all %>% 
  group_by(SampleSite_ID, ID2) %>% 
  filter(Year != 0) %>% 
  summarize(across(MAT:CMI_sm, list(max=max, min=min, mean=mean)))

mmm_sf <- clim.all %>% 
  group_by(SampleSite_ID, ID2) %>% 
  filter(Year != 0) %>% 
  summarize(NFFD_sp = min(NFFD_sp))

mmm_hd <- mmm %>% 
  select(SampleSite_ID, ID2, MAT_max, MWMT_max, MCMT_max, MAP_min, PAS_min, AHM_max, SHM_max, Tmax_sm_max, PPT_sm_min, CMI_sm_min)

mmm_cw <- mmm %>% 
  select(SampleSite_ID, ID2, MAT_min, MWMT_min, MCMT_min, MAP_max, PAS_max, AHM_min, SHM_min, Tmax_sm_min, PPT_sm_max, CMI_sm_max)

mmm_cw$type <- "CW"
mmm_hd$type <- "HD"

mmm_cw <- mmm_cw %>% 
  rename_with(~ str_remove(., "_max|_min"))
mmm_hd <- mmm_hd %>% 
  rename_with(~ str_remove(., "_max|_min"))

mmm <- rbind(mmm_cw,mmm_hd)
mmm1 <- full_join(mmm_cw, mmm_hd, by = "SampleSite_ID")
climate <- left_join(mmm1, bin_dis_GIS1, by="SampleSite_ID"
)

```
# Climate Dataframe For Modelling
```{r}
climate1 <- zscores %>% 
  select( SampleSite_ID, contains("cool.wet"))
climate1 <- left_join(climate1, mmm_hd, by = "SampleSite_ID")
climate1 <- left_join(climate1, mmm_sf, by = "SampleSite_ID")
climate <- left_join(climate1, bin_dis_GIS1, by = "SampleSite_ID")

```





