---
title: "Climate"
author: "Nat"
date: "2024-04-25"
output: html_document
---
# Load dataframes and packages

```{r}
library(tidyverse)
#library(ClimateNAr)
library(sf)

regen <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Regen_2023_ALL.csv"
regen <- read.csv(regen)
site <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Site.csv"
site <- read.csv(site)
GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/GIS_fixed.csv"
GIS <- read.csv(GIS)
internal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Internal.csv"
internal <- read.csv(internal)
basal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/BasalArea.csv"
basal <- read.csv(basal)
regen_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_GIS.csv"
regen_GIS <- read.csv(regen_GIS)
bin_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/binary_GIS.csv"
bin_GIS <- read.csv(bin_GIS)
regen_binary <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_binary.csv"
regen_binary <- read.csv(regen_binary)
actual_coords <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Plot_coordinates_actual.csv"
actual_coords <- read.csv(actual_coords)

```
#Get coords for actual plots
```{r}
#need to convert utm to lat/long

utm_crs <- "+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs"
# Create an sf object
utm_sf <- st_as_sf(actual_coords, coords = c("Easting", "Northing"), crs = utm_crs)

st_crs(utm_sf)

# Convert to latitude/longitude
lat_lon_sf <- st_transform(utm_sf, crs = st_crs("+proj=longlat +datum=WGS84"))
lat_lon_sf <- st_set_precision(lat_lon_sf, 10)

# Extract coordinates and bind to original data
lat_lon_coords <- round(st_coordinates(lat_lon_sf), digits = 10)
lat_lon_data <- cbind(actual_coords, lat_lon_coords)

lat_lon_data <- lat_lon_data %>% 
  rename(#lat = "Y",
         #long = "X",
         Card = "Plot.ID")
#write.csv(lat_lon_data, "C:/Users/nmac2000/Documents/regen project/Data/UTM_Lat_Lon.csv")
```


#Now need to break up by fire year
```{r}
forClim1 <- regen_GIS %>% 
  dplyr::select(Card, Elevation, Fire_Year_1)

forClim1<- full_join(forClim1, lat_lon_data, by="Card")

forClim1 <- forClim1 %>% 
  rename(PlotID = `Card`) %>% 
  dplyr::select(PlotID, Fire_Year_1, lat, long, Elevation) %>% 
  rename(ID1 = "PlotID",
         ID2 = "Fire_Year_1",
         el = "Elevation")

table(forClim1$ID2)

forClim2003 <- forClim1 %>% 
  dplyr::filter(ID2== 2003)
#write.csv(forClim2003, "C:/Users/nmac2000/Documents/regen project/Data/ClimateBC/plots2003.csv")

forClim2009 <- forClim1 %>% 
  filter(ID2== 2009)
#write.csv(forClim2009, "C:/Users/nmac2000/Documents/regen project/Data/ClimateBC/plots2009.csv")

forClim2010 <- forClim1 %>% 
  filter(ID2== 2010)

forClim2015 <- forClim1 %>% 
  filter(ID2== 2015)

forClim2016 <- forClim1 %>% 
  filter(ID2== 2016)

forClim2017 <- forClim1 %>% 
  filter(ID2== 2017)

forClim2023 <- forClim1 %>% 
  filter(ID2== 2023)

## need to break 2017 into multiple data frame for Climate NA
```


```{r}
#clim2003.2004 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2004.ann', MSY='SY')
#clim2003.2005 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2005.ann', MSY='SY')
#clim2003.2006 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2003, period='Year_2006.ann', MSY='SY')
#write.csv(clim2003.2004, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/2004.csv")
clim2003.2004 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2003/2004.csv")
#write.csv(clim2003.2005, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/2005.csv")
clim2003.2005 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2003/2005.csv")
#write.csv(clim2003.2006, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2003/2006.csv")
clim2003.2006 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2003/2006.csv")

#clim2009.2010 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2010.ann', MSY='SY')
#clim2009.2011 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2011.ann', MSY='SY')
#clim2009.2012 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2009, period='Year_2012.ann', MSY='SY')
#write.csv(clim2009.2010, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2010.csv")
clim2009.2010 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2010.csv")
#write.csv(clim2009.2011, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2011.csv")
clim2009.2011 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2011.csv")
#write.csv(clim2009.2012, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2009/2012.csv")
clim2009.2012 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2009/2012.csv")

#clim2010.2011 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2011.ann', MSY='SY')
#clim2010.2012 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2012.ann', MSY='SY')
#clim2010.2013 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2010, period='Year_2013.ann', MSY='SY')
#write.csv(clim2010.2011, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2011.csv")
clim2010.2011 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2011.csv")
#write.csv(clim2010.2012, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2012.csv")
clim2010.2012 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2012.csv")
#write.csv(clim2010.2013, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2010/2013.csv")
clim2010.2013 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2010/2013.csv")

#clim2015.2016 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2016.ann', MSY='SY')
#clim2015.2017 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2017.ann', MSY='SY')
#clim2015.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2015, period='Year_2018.ann', MSY='SY')
#write.csv(clim2015.2016, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2016.csv")
clim2015.2016 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2016.csv")
#write.csv(clim2015.2017, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2017.csv")
clim2015.2017 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2017.csv")
#write.csv(clim2015.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2015/2018.csv")
clim2015.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2015/2018.csv")

#clim2016.2017 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2017.ann', MSY='SY')
#clim2016.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2018.ann', MSY='SY')
#clim2016.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2016, period='Year_2019.ann', MSY='SY')
#write.csv(clim2016.2017, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2017.csv")
clim2016.2017 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2017.csv")
#write.csv(clim2016.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2018.csv")
clim2016.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2018.csv")
#write.csv(clim2016.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2016/2019.csv")
clim2016.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2016/2019.csv")


###2017 data needs to be split up
forClim2017a <- forClim2017[1:100,]
forClim2017b <- forClim2017[101:200,]
forClim2017c <- forClim2017[201:277,]

#clim2017a.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2018.ann', MSY='SY')
#clim2017a.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2019.ann', MSY='SY')
#clim2017a.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017a, period='Year_2020.ann', MSY='SY')
#write.csv(clim2017a.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2018a.csv")
clim2017a.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2018a.csv")
#write.csv(clim2017a.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2019a.csv")
clim2017a.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2019a.csv")
#write.csv(clim2017a.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2020a.csv")
clim2017a.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2020a.csv")

#clim2017b.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2018.ann', MSY='SY')
#clim2017b.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2019.ann', MSY='SY')
#clim2017b.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017b, period='Year_2020.ann', MSY='SY')
#write.csv(clim2017b.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2018b.csv")
clim2017b.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2018b.csv")
#write.csv(clim2017b.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2019b.csv")
clim2017b.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2019b.csv")
#write.csv(clim2017b.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2020b.csv")
clim2017b.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2020b.csv")

#clim2017c.2018 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2018.ann', MSY='SY')
#clim2017c.2019 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2019.ann', MSY='SY')
#clim2017c.2020 <- ClimateNA_API2(ClimateBC_NA='BC', forClim2017c, period='Year_2020.ann', MSY='SY')
#write.csv(clim2017c.2018, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2018c.csv")
clim2017c.2018 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2018c.csv")
#write.csv(clim2017c.2019, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2019c.csv")
clim2017c.2019 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2019c.csv")
#write.csv(clim2017c.2020, "C:/Users/nmac2000/Documents/regen project/Regen/Data/ClimateBC/2017/2020c.csv")
clim2017c.2020 <- read.csv("https://raw.githubusercontent.com/nmac2000/Regen/main/Data/ClimateBC/2017/2020c.csv")
```
#need to now make compiled data frame for each year and find mins, maxs, and avgs
variables of interest:
  -MAT mean annual temperature
  -MWMT mean warmest month temperature
  -MCMT mean coldest month temperature
  -NFFD number of frost free days
  -PAS precipitation as snow
  -Eref Hargreaves reference evaporation
  -CMD Hargreaves climatic moisture deficit
  -AHM annual heat-moisture index
  -SHM summer heat-moisture index
  -Tave_sp spring mean temp
  -Tave_sm summer mean temp
  -Tmax_sp spring max temp
  -Tmax_sm summer max temp
  -Tmin_sp spring min temp
  -Tmin_sm summer min temp
  -PPT_wt winter precipitation
  -PPT_sp spring precipitation
  -PPT_sm summer precipitation
  -NFFD_sp spring number of frost free days
  -PAS_wt
  -PAS_sp spring precipitation as snow
  -Eref_sm summer Hargreaves reference evaporation
  -CMD_sm summer Hargreaves climatic moisture deficit
  -CMI_sm Summer Hogg's climate moisture index 
  
  
  
  
```{r}
select(MAT, MWMT, MCMT, NFFD, PAS, Eref, CMD, AHM, SHM, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, 
       Tmin_sp, Tmin_sm, PPT_wt, PPT_sp, PPT_sm, NFFD_sp, PAS_wt, PAS_sp, Eref_sm, CMD_sm, CMI_sm)

set.seed(123)
a <- data.frame(matrix(sample(20,10), ncol = 5, nrow = 5))
b <- data.frame(matrix(sample(20,10), ncol = 5, nrow = 5))
c <- data.frame(matrix(sample(20,10), ncol = 5, nrow = 5))




```

#Combine different years
```{r}
#2017 had 3 different df because it was so large
clim2017.2018 <- rbind(clim2017a.2018,clim2017b.2018,clim2017c.2018)
clim2017.2018$Year <- 1

clim2017a.2019 <- subset(clim2017a.2019, select = -c(X.1))
clim2017.2019 <- rbind(clim2017a.2019,clim2017b.2019,clim2017c.2019)
clim2017.2019$Year <- 2

clim2017.2020 <- rbind(clim2017a.2020,clim2017b.2020,clim2017c.2020)
clim2017.2020$Year <- 3

clim2017 <- rbind(clim2017.2018, clim2017.2019, clim2017.2020)

#2003
clim2003.2004$Year <- 1
clim2003.2005$Year <-2
clim2003.2006$Year <-3
clim2003 <- rbind(clim2003.2004,clim2003.2005,clim2003.2006)

#2009
clim2009.2010$Year <- 1
clim2009.2011$Year <-2
clim2009.2012$Year <-3
clim2009 <- rbind(clim2009.2010,clim2009.2011,clim2009.2012)

#2010
clim2010.2011$Year <- 1
clim2010.2012$Year <-2
clim2010.2013$Year <-3
clim2010 <- rbind(clim2010.2011,clim2010.2012,clim2010.2013)

#2015
clim2015.2016$Year <- 1
clim2015.2017$Year <-2
clim2015.2018$Year <-3
clim2015 <- rbind(clim2015.2016,clim2015.2017,clim2015.2018)

#2016
clim2016.2017$Year <- 1
clim2016.2018$Year <-2
clim2016.2019$Year <-3
clim2016 <- rbind(clim2016.2017,clim2016.2018,clim2016.2019)

```

#test select because I forgot to push my code from my other computer
```{r}
clim2003 <- clim2003 %>% 
  select(ID1, MAT, MWMT, MAP, NFFD, PAS, Eref, CMD, CMI, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp)

clim2003.summary <- clim2003 %>% 
  group_by(ID1) %>% 
  summarize(MAT.av = mean(MAT),
         MAT.min = min(MAT),
         MAT.max = max(MAT),
         MWMT.av = mean(MWMT),
         MWMT.min = min(MWMT),
         MWMT.max = max(MWMT),
         MAP.av = mean(MAP),
         MAP.min = min(MAP),
         MAP.max = max(MAP),
         NFFD.av = mean(NFFD),
         NFFD.min = min(NFFD),
         NFFD.max = max(NFFD),
         PAS.av = mean(PAS),
         PAS.min = min(PAS),
         PAS.max = max(PAS),
         Eref.av = mean(Eref),
         Eref.min = min(Eref),
         Eref.max = max(Eref),
         CMD.av = mean(CMD),
         CMD.min = min(CMD),
         CMD.max = max(CMD),
         CMI.av = mean(CMI),
         CMI.min = min(CMI),
         CMI.max = max(CMI),
         Tave_sp.av = mean(Tave_sp),
         Tave_sp.min = min(Tave_sp),
         Tave_sp.max = max(Tave_sp),
         Tave_sm.av = mean(Tave_sm),
         Tave_sm.min = min(Tave_sm),
         Tave_sm.max = max(Tave_sm),
         Tmax_sp.av = mean(Tmax_sp),
         Tmax_sp.min = min(Tmax_sp),
         Tmax_sp.max = max(Tmax_sp),
         Tmax_sm.av = mean(Tmax_sm),
         Tmax_sm.min = min(Tmax_sm),
         Tmax_sm.max = max(Tmax_sm),
         Tmin_sp.av = mean(Tmin_sp),
         Tmin_sp.min = min(Tmin_sp),
         Tmin_sp.max = max(Tmin_sp),
         Tmin_sm.av = mean(Tmin_sm),
         Tmin_sm.min = min(Tmin_sm),
         Tmin_sm.max = max(Tmin_sm),
         NFFD_sp.av = mean(NFFD_sp),
         NFFD_sp.min = min(NFFD_sp),
         NFFD_sp.max = max(NFFD_sp),
         PAS_sp.av = mean(PAS_sp),
         PAS_sp.min = min(PAS_sp),
         PAS_sp.max = max(PAS_sp)) %>% 
  select(ID1, MAT.av:last_col())

#2005
clim2009 <- clim2009 %>% 
  select(ID1, MAT, MWMT, MAP, NFFD, PAS, Eref, CMD, CMI, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp)

clim2009.summary <- clim2009 %>% 
  group_by(ID1) %>% 
  summarize(MAT.av = mean(MAT),
         MAT.min = min(MAT),
         MAT.max = max(MAT),
         MWMT.av = mean(MWMT),
         MWMT.min = min(MWMT),
         MWMT.max = max(MWMT),
         MAP.av = mean(MAP),
         MAP.min = min(MAP),
         MAP.max = max(MAP),
         NFFD.av = mean(NFFD),
         NFFD.min = min(NFFD),
         NFFD.max = max(NFFD),
         PAS.av = mean(PAS),
         PAS.min = min(PAS),
         PAS.max = max(PAS),
         Eref.av = mean(Eref),
         Eref.min = min(Eref),
         Eref.max = max(Eref),
         CMD.av = mean(CMD),
         CMD.min = min(CMD),
         CMD.max = max(CMD),
         CMI.av = mean(CMI),
         CMI.min = min(CMI),
         CMI.max = max(CMI),
         Tave_sp.av = mean(Tave_sp),
         Tave_sp.min = min(Tave_sp),
         Tave_sp.max = max(Tave_sp),
         Tave_sm.av = mean(Tave_sm),
         Tave_sm.min = min(Tave_sm),
         Tave_sm.max = max(Tave_sm),
         Tmax_sp.av = mean(Tmax_sp),
         Tmax_sp.min = min(Tmax_sp),
         Tmax_sp.max = max(Tmax_sp),
         Tmax_sm.av = mean(Tmax_sm),
         Tmax_sm.min = min(Tmax_sm),
         Tmax_sm.max = max(Tmax_sm),
         Tmin_sp.av = mean(Tmin_sp),
         Tmin_sp.min = min(Tmin_sp),
         Tmin_sp.max = max(Tmin_sp),
         Tmin_sm.av = mean(Tmin_sm),
         Tmin_sm.min = min(Tmin_sm),
         Tmin_sm.max = max(Tmin_sm),
         NFFD_sp.av = mean(NFFD_sp),
         NFFD_sp.min = min(NFFD_sp),
         NFFD_sp.max = max(NFFD_sp),
         PAS_sp.av = mean(PAS_sp),
         PAS_sp.min = min(PAS_sp),
         PAS_sp.max = max(PAS_sp)) %>% 
  select(ID1, MAT.av:last_col())

#2010
clim2010 <- clim2010 %>% 
  select(ID1, MAT, MWMT, MAP, NFFD, PAS, Eref, CMD, CMI, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp)

clim2010.summary <- clim2010 %>% 
  group_by(ID1) %>% 
  summarize(MAT.av = mean(MAT),
         MAT.min = min(MAT),
         MAT.max = max(MAT),
         MWMT.av = mean(MWMT),
         MWMT.min = min(MWMT),
         MWMT.max = max(MWMT),
         MAP.av = mean(MAP),
         MAP.min = min(MAP),
         MAP.max = max(MAP),
         NFFD.av = mean(NFFD),
         NFFD.min = min(NFFD),
         NFFD.max = max(NFFD),
         PAS.av = mean(PAS),
         PAS.min = min(PAS),
         PAS.max = max(PAS),
         Eref.av = mean(Eref),
         Eref.min = min(Eref),
         Eref.max = max(Eref),
         CMD.av = mean(CMD),
         CMD.min = min(CMD),
         CMD.max = max(CMD),
         CMI.av = mean(CMI),
         CMI.min = min(CMI),
         CMI.max = max(CMI),
         Tave_sp.av = mean(Tave_sp),
         Tave_sp.min = min(Tave_sp),
         Tave_sp.max = max(Tave_sp),
         Tave_sm.av = mean(Tave_sm),
         Tave_sm.min = min(Tave_sm),
         Tave_sm.max = max(Tave_sm),
         Tmax_sp.av = mean(Tmax_sp),
         Tmax_sp.min = min(Tmax_sp),
         Tmax_sp.max = max(Tmax_sp),
         Tmax_sm.av = mean(Tmax_sm),
         Tmax_sm.min = min(Tmax_sm),
         Tmax_sm.max = max(Tmax_sm),
         Tmin_sp.av = mean(Tmin_sp),
         Tmin_sp.min = min(Tmin_sp),
         Tmin_sp.max = max(Tmin_sp),
         Tmin_sm.av = mean(Tmin_sm),
         Tmin_sm.min = min(Tmin_sm),
         Tmin_sm.max = max(Tmin_sm),
         NFFD_sp.av = mean(NFFD_sp),
         NFFD_sp.min = min(NFFD_sp),
         NFFD_sp.max = max(NFFD_sp),
         PAS_sp.av = mean(PAS_sp),
         PAS_sp.min = min(PAS_sp),
         PAS_sp.max = max(PAS_sp)) %>% 
  select(ID1, MAT.av:last_col())

#2015
clim2015 <- clim2015 %>% 
  select(ID1, MAT, MWMT, MAP, NFFD, PAS, Eref, CMD, CMI, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp)

clim2015.summary <- clim2015 %>% 
  group_by(ID1) %>% 
  summarize(MAT.av = mean(MAT),
         MAT.min = min(MAT),
         MAT.max = max(MAT),
         MWMT.av = mean(MWMT),
         MWMT.min = min(MWMT),
         MWMT.max = max(MWMT),
         MAP.av = mean(MAP),
         MAP.min = min(MAP),
         MAP.max = max(MAP),
         NFFD.av = mean(NFFD),
         NFFD.min = min(NFFD),
         NFFD.max = max(NFFD),
         PAS.av = mean(PAS),
         PAS.min = min(PAS),
         PAS.max = max(PAS),
         Eref.av = mean(Eref),
         Eref.min = min(Eref),
         Eref.max = max(Eref),
         CMD.av = mean(CMD),
         CMD.min = min(CMD),
         CMD.max = max(CMD),
         CMI.av = mean(CMI),
         CMI.min = min(CMI),
         CMI.max = max(CMI),
         Tave_sp.av = mean(Tave_sp),
         Tave_sp.min = min(Tave_sp),
         Tave_sp.max = max(Tave_sp),
         Tave_sm.av = mean(Tave_sm),
         Tave_sm.min = min(Tave_sm),
         Tave_sm.max = max(Tave_sm),
         Tmax_sp.av = mean(Tmax_sp),
         Tmax_sp.min = min(Tmax_sp),
         Tmax_sp.max = max(Tmax_sp),
         Tmax_sm.av = mean(Tmax_sm),
         Tmax_sm.min = min(Tmax_sm),
         Tmax_sm.max = max(Tmax_sm),
         Tmin_sp.av = mean(Tmin_sp),
         Tmin_sp.min = min(Tmin_sp),
         Tmin_sp.max = max(Tmin_sp),
         Tmin_sm.av = mean(Tmin_sm),
         Tmin_sm.min = min(Tmin_sm),
         Tmin_sm.max = max(Tmin_sm),
         NFFD_sp.av = mean(NFFD_sp),
         NFFD_sp.min = min(NFFD_sp),
         NFFD_sp.max = max(NFFD_sp),
         PAS_sp.av = mean(PAS_sp),
         PAS_sp.min = min(PAS_sp),
         PAS_sp.max = max(PAS_sp)) %>% 
  select(ID1, MAT.av:last_col())

#2016
clim2016 <- clim2016 %>% 
  select(ID1, MAT, MWMT, MAP, NFFD, PAS, Eref, CMD, CMI, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp)

clim2016.summary <- clim2016 %>% 
  group_by(ID1) %>% 
  summarize(MAT.av = mean(MAT),
         MAT.min = min(MAT),
         MAT.max = max(MAT),
         MWMT.av = mean(MWMT),
         MWMT.min = min(MWMT),
         MWMT.max = max(MWMT),
         MAP.av = mean(MAP),
         MAP.min = min(MAP),
         MAP.max = max(MAP),
         NFFD.av = mean(NFFD),
         NFFD.min = min(NFFD),
         NFFD.max = max(NFFD),
         PAS.av = mean(PAS),
         PAS.min = min(PAS),
         PAS.max = max(PAS),
         Eref.av = mean(Eref),
         Eref.min = min(Eref),
         Eref.max = max(Eref),
         CMD.av = mean(CMD),
         CMD.min = min(CMD),
         CMD.max = max(CMD),
         CMI.av = mean(CMI),
         CMI.min = min(CMI),
         CMI.max = max(CMI),
         Tave_sp.av = mean(Tave_sp),
         Tave_sp.min = min(Tave_sp),
         Tave_sp.max = max(Tave_sp),
         Tave_sm.av = mean(Tave_sm),
         Tave_sm.min = min(Tave_sm),
         Tave_sm.max = max(Tave_sm),
         Tmax_sp.av = mean(Tmax_sp),
         Tmax_sp.min = min(Tmax_sp),
         Tmax_sp.max = max(Tmax_sp),
         Tmax_sm.av = mean(Tmax_sm),
         Tmax_sm.min = min(Tmax_sm),
         Tmax_sm.max = max(Tmax_sm),
         Tmin_sp.av = mean(Tmin_sp),
         Tmin_sp.min = min(Tmin_sp),
         Tmin_sp.max = max(Tmin_sp),
         Tmin_sm.av = mean(Tmin_sm),
         Tmin_sm.min = min(Tmin_sm),
         Tmin_sm.max = max(Tmin_sm),
         NFFD_sp.av = mean(NFFD_sp),
         NFFD_sp.min = min(NFFD_sp),
         NFFD_sp.max = max(NFFD_sp),
         PAS_sp.av = mean(PAS_sp),
         PAS_sp.min = min(PAS_sp),
         PAS_sp.max = max(PAS_sp)) %>% 
  select(ID1, MAT.av:last_col())

#2017
clim2017 <- clim2017 %>% 
  select(ID1, MAT, MWMT, MAP, NFFD, PAS, Eref, CMD, CMI, Tave_sp, Tave_sm, Tmax_sp, Tmax_sm, Tmin_sp,
         Tmin_sm, NFFD_sp, PAS_sp)

clim2017.summary <- clim2017 %>% 
  group_by(ID1) %>% 
  summarize(MAT.av = mean(MAT),
         MAT.min = min(MAT),
         MAT.max = max(MAT),
         MWMT.av = mean(MWMT),
         MWMT.min = min(MWMT),
         MWMT.max = max(MWMT),
         MAP.av = mean(MAP),
         MAP.min = min(MAP),
         MAP.max = max(MAP),
         NFFD.av = mean(NFFD),
         NFFD.min = min(NFFD),
         NFFD.max = max(NFFD),
         PAS.av = mean(PAS),
         PAS.min = min(PAS),
         PAS.max = max(PAS),
         Eref.av = mean(Eref),
         Eref.min = min(Eref),
         Eref.max = max(Eref),
         CMD.av = mean(CMD),
         CMD.min = min(CMD),
         CMD.max = max(CMD),
         CMI.av = mean(CMI),
         CMI.min = min(CMI),
         CMI.max = max(CMI),
         Tave_sp.av = mean(Tave_sp),
         Tave_sp.min = min(Tave_sp),
         Tave_sp.max = max(Tave_sp),
         Tave_sm.av = mean(Tave_sm),
         Tave_sm.min = min(Tave_sm),
         Tave_sm.max = max(Tave_sm),
         Tmax_sp.av = mean(Tmax_sp),
         Tmax_sp.min = min(Tmax_sp),
         Tmax_sp.max = max(Tmax_sp),
         Tmax_sm.av = mean(Tmax_sm),
         Tmax_sm.min = min(Tmax_sm),
         Tmax_sm.max = max(Tmax_sm),
         Tmin_sp.av = mean(Tmin_sp),
         Tmin_sp.min = min(Tmin_sp),
         Tmin_sp.max = max(Tmin_sp),
         Tmin_sm.av = mean(Tmin_sm),
         Tmin_sm.min = min(Tmin_sm),
         Tmin_sm.max = max(Tmin_sm),
         NFFD_sp.av = mean(NFFD_sp),
         NFFD_sp.min = min(NFFD_sp),
         NFFD_sp.max = max(NFFD_sp),
         PAS_sp.av = mean(PAS_sp),
         PAS_sp.min = min(PAS_sp),
         PAS_sp.max = max(PAS_sp)) %>% 
  select(ID1, MAT.av:last_col())

```



