---
title: "Models"
author: '3034081184'
date: "2024-05-23"
output: html_document
---

```{r}
#need to figure out data frames for everything and clean up code
bin_dis_GIS1 <- bin_dis_GIS %>%
  distinct(SampleSite_ID, .keep_all = T)

```

structural
```{r}
names(bin_dis_GIS1)  # print out the column (i.e., variable) names
dim(bin_dis_GIS1)    # number of rows and columns
head(bin_dis_GIS1)  # print out the first few lines of data

#need to put this somewhere else later on
bin_dis_GIS1$DISTURBANCE_TYPE_1<- sub( "IBM  ", "IBM", bin_dis_GIS1$DISTURBANCE_TYPE_1)

# ensure y variable is a factor for dead versus alive
bin_dis_GIS1$PLI.f <- as.factor(bin_dis_GIS1$PLI_count_bin)
bin_dis_GIS1$FDI.f <- as.factor(bin_dis_GIS1$FDI_count_bin)
# y=1 for dead trees, y=0 for live trees
class(bin_dis_GIS1$PLI.f)
bin_dis_GIS1$Distance <- as.numeric(bin_dis_GIS1$Distance)
bin_dis_GIS1$CROWN_CLOSURE_1 <- as.numeric(bin_dis_GIS1$CROWN_CLOSURE_1)
bin_dis_GIS1$PROJ_AGE_1_1 <- as.numeric(bin_dis_GIS1$PROJ_AGE_1_1)
bin_dis_GIS1$PROJ_HEIGHT_1_1 <- as.numeric(bin_dis_GIS1$PROJ_HEIGHT_1_1)
bin_dis_GIS1$DISTANCE_TO_PERIMETER <- as.numeric(bin_dis_GIS1$DISTANCE_TO_PERIMETER)
bin_dis_GIS1$years_since <- as.numeric(2023-bin_dis_GIS1$FIRE_YEAR_1)
bin_dis_GIS1$DISTURBANCE_TYPE_1 <- as.factor(bin_dis_GIS1$DISTURBANCE_TYPE_1)
bin_dis_GIS1$BURN_SEVERITY_RATING_1 <- factor(bin_dis_GIS1$BURN_SEVERITY_RATING_1, 
                                                 levels = c("Unburned", "Low", "Medium", "High", "Unknown"))
bin_dis_GIS1$SPECIES_CD_1_1 <- factor(bin_dis_GIS1$SPECIES_CD_1_1, levels = c("PLI", "FDI", "AT", "SX"))

#bin_dis_GIS1 <- bin_dis_GIS1 %>% 
#  filter(!is.na(Distance), !is.na(years_since), !is.na(CROWN_CLOSURE_1),
         !is.na(PROJ_AGE_1_1), !is.na(PROJ_HEIGHT_1_1), !is.na(DISTURBANCE_TYPE_1),
         !is.na(DISTANCE_TO_PERIMETER), !is.na(BURN_SEVERITY_RATING_1),
         !is.na(PLI.f), !is.na(FDI.f), !is.na(MEAN))
```

Step 1
```{r}
structure.PLI.full <- glm(PLI.f ~ Distance + years_since + CROWN_CLOSURE_1 + PROJ_AGE_1_1 + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        BURN_SEVERITY_RATING_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.full)

logistic.null <- glm(PLI.f ~ 1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(logistic.null)

structure.PLIa <- glm(PLI.f ~ Distance ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIa) #not significant on own

structure.PLIb <- glm(PLI.f ~ years_since ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIb) #significant on own

structure.PLIc <- glm(PLI.f ~ CROWN_CLOSURE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIc) #not significant on own

structure.PLId <- glm(PLI.f ~ PROJ_AGE_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLId) #significant on own

structure.PLIe <- glm(PLI.f ~ PROJ_HEIGHT_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIe) #significant on own

structure.PLIf <- glm(PLI.f ~ DISTURBANCE_TYPE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIf) #significant on own 


structure.PLIg <- glm(PLI.f ~ DISTANCE_TO_PERIMETER ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIg) #significant on own

structure.PLIh <- glm(PLI.f ~ BURN_SEVERITY_RATING_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIh) #significant on own

structure.PLIi <- glm(PLI.f ~ MEAN ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIi)

structure.PLIj <- glm(PLI.f ~ SPECIES_CD_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIj)

structure.PLIk <- glm(PLI.f ~ PATCH_SIZE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIk)

structure.PLIl <- glm(PLI.f ~ SPECIES_PCT_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIl)

structure.PLIm <- glm(PLI.f ~ SPECIES_CD_2_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIm)

structure.PLIn <- glm(PLI.f ~ SPECIES_CD_3_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLIn)

lrtest(structure.PLIj, logistic.null)
lrtest(structure.PLIm, logistic.null)
lrtest(structure.PLIn, logistic.null)
```
Compare categorical variables to null model
```{r}
library(lmtest)
lrtest(structure.PLIf, logistic.null)
lrtest(structure.PLIh, logistic.null)
```

Step 2
```{r}
structure.PLI.1a <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        BURN_SEVERITY_RATING_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.1a)

structure.PLI.1aNull1 <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTANCE_TO_PERIMETER + 
                        BURN_SEVERITY_RATING_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
structure.PLI.1aNull2 <-glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)

lrtest(structure.PLI.1a, structure.PLI.1aNull1)
lrtest(structure.PLI.1a, structure.PLI.1aNull2)

structure.PLI.2a <- glm(PLI.f ~    years_since  + PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + BURN_SEVERITY_RATING_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.2a)

structure.PLI.2aNull1 <- glm(PLI.f ~ years_since  + PROJ_HEIGHT_1_1 + BURN_SEVERITY_RATING_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
structure.PLI.2aNull2 <- glm(PLI.f ~ years_since  + PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)

lrtest(structure.PLI.2a, structure.PLI.2aNull1)
lrtest(structure.PLI.2a, structure.PLI.2aNull2)
lrtest(structure.PLI.1a, structure.PLI.2a)
```

Step 2 with dNBR
```{r}
structure.PLI.2b <- glm(PLI.f ~ PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.2b)

structure.PLI.1b <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        MAX ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.1b)

structure.PLI.2c <- glm(PLI.f ~    years_since  + PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + MEAN ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.2c)

lrtest(structure.PLI.1b, structure.PLI.2c)
```

```{r}
structure.PLI.1c <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        MEAN + PATCH_SIZE_1 + SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.1c)

structure.PLI.1d <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        MAX + PATCH_SIZE_1 + SPECIES_CD_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.1d)

lrtest(structure.PLI.1c, structure.PLI.1d)

structure.PLI.1e <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        MAX + PATCH_SIZE_1 + SPECIES_CD_1_2 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.1e)

lrtest(structure.PLI.1c, structure.PLI.1e)

structure.PLI.1f <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTANCE_TO_PERIMETER + 
                        MAX + PATCH_SIZE_1 + SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.1f)

lrtest(structure.PLI.1c, structure.PLI.1f)

structure.PLI.2d <- glm(PLI.f ~   years_since  + PROJ_HEIGHT_1_1 + MEAN + SPECIES_CD_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.2d)

structure.PLI.2e <- glm(PLI.f ~   years_since  + PROJ_HEIGHT_1_1 + MEAN  ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.2e)
lrtest(structure.PLI.2d, structure.PLI.2e)
lrtest(structure.PLI.2d, structure.PLI.1c)


structure.PLI.3a <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        MEAN + PATCH_SIZE_1 + SPECIES_CD_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.3a)

structure.PLI.3b <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        MEAN +  SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.3b)

structure.PLI.3c <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 +  
                        MEAN +  SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.3c)

structure.PLI.3d <- glm(PLI.f ~   Distance + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTANCE_TO_PERIMETER +  
                        MEAN +  SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.3d)


structure.PLI.3e <- glm(PLI.f ~   DISTURBANCE_TYPE_1 + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTANCE_TO_PERIMETER +  
                        MEAN +  SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.3e)

structure.PLI.3f <- glm(PLI.f ~  Distance + DISTURBANCE_TYPE_1 + years_since  + 
                        PROJ_HEIGHT_1_1 + DISTANCE_TO_PERIMETER +  
                        MEAN +  SPECIES_CD_1_1 + SPECIES_CD_2_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.3f)
lrtest(structure.PLI.2d, structure.PLI.3f)
```
```
Step 4 attempt 3
```{r}
structure.PLI.4a <- glm(PLI.f ~  BURN_SEVERITY_RATING_1 + years_since  + PROJ_HEIGHT_1_1 + MEAN + SPECIES_CD_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.PLI.4a)
lrtest(structure.PLI.4a,structure.PLI.2d)
```







```{r}
bin_dis_GIS1$linpred.GLM2a <- predict(structure.PLI.2d) # Estimated logit using the linear part
bin_dis_GIS1$yhat.GLM2a <- fitted(structure.PLI.2d) # Estimated probability using inverse logityhat values
bin_dis_GIS1$resid.GLM2a <- resid(structure.PLI.2d) # the deviances 

# Graph of predicted probabilities ranges for dead versus alive
# Would like the dead=0 (it is alive) trees to have all low predicted prob(dead) 
# and the dead=1 (it is dead) trees to all have high predicted prob (dead). 
par(mfrow=c(1,1),mai=c(1,1,0.6,0.6),cex=0.8)
plot(bin_dis_GIS1$PLI.f,bin_dis_GIS1$yhat.GLM2a,pch=8,
  main="Model 1: Predicted Prob for Seedling Occurrence (PLI)",
  ylab="Predicted Prob(occurrence)", xlab="Seedling (=1) or No seedling(=0) as Recorded")
par(mfrow=c(1,1),mai=c(1,1,1,1),cex=1)
```

```{r}
# GLM1
cutoff <- 0.7 # you can play around with different cutoff values
n <- dim(bin_dis_GIS1)[1]
bin_dis_GIS1$PLI_count_bin <- as.numeric(levels(bin_dis_GIS1$PLI_count_bin))[bin_dis_GIS1$PLI_count_bin]
obs <- bin_dis_GIS1$PLI_count_bin
pred <- ifelse(bin_dis_GIS1$yhat.GLM2a >= cutoff, 1,0)

bin_dis_GIS1$GLM2a <- ifelse( obs == 1 & (obs - pred) == 0, 1, 0) ; a <- sum(bin_dis_GIS1$GLM2a) # a: true positives
bin_dis_GIS1$GLM2c <- ifelse( obs == 1 & (obs - pred) == 1, 1, 0) ; c <- sum(bin_dis_GIS1$GLM2c) # c: false negative
bin_dis_GIS1$GLM2b <- ifelse( obs == 0 & (obs - pred) == -1, 1, 0) ; b <- sum(bin_dis_GIS1$GLM2b) # b: false positives
bin_dis_GIS1$GLM2d <- ifelse( obs == 0 & (obs - pred) == 0, 1, 0) ; d <- sum(bin_dis_GIS1$GLM2d) # d: true negatives

# general confusion matrix layout
matrix(c("a","c" , "b","d"), nrow=2, ncol=2)
CM.GLM2 <- matrix(c(a,c , b,d), nrow=2, ncol=2)
CM.GLM2



# overall accuracy = (a+d)/n
GLM2.oa <- (a+d)/n
GLM2.sensitivity <- a/(a+c)
GLM2.specificity <- d/(b+d)
kappa.bit <- (a+b)*(a+c)+(c+d)*(d+b)
GLM2.kappa <- (  ((a+d)/n)  - (kappa.bit/n^2) ) / (1- (kappa.bit/n^2) )
GLM2.TSS <- GLM2.sensitivity + GLM2.specificity -1

GLM2.predacc <- c(GLM2.oa, GLM2.sensitivity, GLM2.specificity, GLM2.kappa,GLM2.TSS)

GLM2.auc <-pROC::auc(bin_dis_GIS1$PLI_count_bin,bin_dis_GIS1$yhat.GLM2a)
plot(pROC::roc(bin_dis_GIS1$PLI_count_bin,bin_dis_GIS1$yhat.GLM2a),auc.polygon=T)
```

```{r}
bin_dis_GIS1$linpred.GLM1a1 <- predict(structure.PLIa1) # Estimated logit using the linear part
bin_dis_GIS1$yhat.GLM1a1 <- fitted(structure.PLIa1) # Estimated probability using inverse logityhat values
bin_dis_GIS1$resid.GLM1a1 <- resid(structure.PLIa1) # the deviances 

cutoff <- 0.8 # you can play around with different cutoff values
n <- dim(bin_dis_GIS1)[1]
obs <- bin_dis_GIS1$PLI_count_bin
pred <- ifelse(bin_dis_GIS1$yhat.GLM1a1 >= cutoff, 1,0)

bin_dis_GIS1$GLM1a <- ifelse( obs == 1 & (obs - pred) == 0, 1, 0) ; a <- sum(bin_dis_GIS1$GLM1a) # a: true positives
bin_dis_GIS1$GLM1c <- ifelse( obs == 1 & (obs - pred) == 1, 1, 0) ; c <- sum(bin_dis_GIS1$GLM1c) # c: false negative
bin_dis_GIS1$GLM1b <- ifelse( obs == 0 & (obs - pred) == -1, 1, 0) ; b <- sum(bin_dis_GIS1$GLM1b) # b: false positives
bin_dis_GIS1$GLM1d <- ifelse( obs == 0 & (obs - pred) == 0, 1, 0) ; d <- sum(bin_dis_GIS1$GLM1d) # d: true negatives

# general confusion matrix layout
matrix(c("a","c" , "b","d"), nrow=2, ncol=2)
CM.GLM1 <- matrix(c(a,c , b,d), nrow=2, ncol=2)
CM.GLM1



# overall accuracy = (a+d)/n
GLM1a1.oa <- (a+d)/n
GLM1a1.sensitivity <- a/(a+c)
GLM1a1.specificity <- d/(b+d)
kappa.bit <- (a+b)*(a+c)+(c+d)*(d+b)
GLM1a1.kappa <- (  ((a+d)/n)  - (kappa.bit/n^2) ) / (1- (kappa.bit/n^2) )
GLM1a1.TSS <- GLM1.sensitivity + GLM1.specificity -1

GLM1.predacc <- c(GLM1.oa, GLM1.sensitivity, GLM1.specificity, GLM1.kappa,GLM1.TSS)

GLM1.auc <-pROC::auc(bin_dis_GIS1$PLI_count_bin,bin_dis_GIS1$yhat.GLM1a1)
plot(pROC::roc(bin_dis_GIS1$PLI_count_bin,bin_dis_GIS1$yhat.GLM1a1),auc.polygon=T)
#GLM1a1.predacc <- c(GLM1a1.oa, GLM1a1.sensitivity, GLM1a1.specificity, GLM1a1.kappa,GLM1a1.TSS,GLM1a1.auc)
```

FDI
```{r}
structure.FDI.full <- glm(FDI.f ~ Distance + years_since + CROWN_CLOSURE_1 + PROJ_AGE_1_1 + 
                        PROJ_HEIGHT_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        BURN_SEVERITY_RATING_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDI.full)

logistic.null <- glm(FDI.f ~ 1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(logistic.null)

structure.FDIa <- glm(FDI.f ~ Distance ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIa) #significant on own

structure.FDIb <- glm(FDI.f ~ years_since ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIb) #significant on own

structure.FDIc <- glm(FDI.f ~ CROWN_CLOSURE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIc) #not significant on own

structure.FDId <- glm(FDI.f ~ PROJ_AGE_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDId) #significant on own

structure.FDIe <- glm(FDI.f ~ PROJ_HEIGHT_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIe) #significant on own

structure.FDIf <- glm(FDI.f ~ DISTURBANCE_TYPE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIf) #borderline significant on own 


structure.FDIg <- glm(FDI.f ~ DISTANCE_TO_PERIMETER ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIg) #borderline significant on own

structure.FDIh <- glm(FDI.f ~ BURN_SEVERITY_RATING_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIh) #significant on own

structure.FDIi <- glm(FDI.f ~ MEAN ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIi) #not significant on own

structure.FDIj <- glm(FDI.f ~ SPECIES_CD_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIj) #significant on own

structure.FDIk <- glm(FDI.f ~ PATCH_SIZE_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIk)  #borderline significant on own

structure.FDIl <- glm(FDI.f ~ SPECIES_PCT_1_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIl) #significant on own

structure.FDIm <- glm(FDI.f ~ SPECIES_CD_2_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIm) #significant on own

structure.FDIn <- glm(FDI.f ~ SPECIES_CD_3_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDIn) #borderline significant on own


```

Compare categorical variables to null model
```{r}
library(lmtest)
lrtest(structure.FDIf, logistic.null)
lrtest(structure.FDIh, logistic.null)
lrtest(structure.FDIj, logistic.null)
lrtest(structure.FDIm, logistic.null)
lrtest(structure.FDIn, logistic.null)
```
Step 2
```{r}
structure.FDI.1a <- glm(FDI.f ~ Distance + years_since + PROJ_AGE_1_1 + DISTURBANCE_TYPE_1 + DISTANCE_TO_PERIMETER + 
                        BURN_SEVERITY_RATING_1 + MEAN + SPECIES_CD_1_1 +SPECIES_CD_2_1 + SPECIES_CD_3_1 + SPECIES_PCT_1_1,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDI.1a)

structure.FDI.2a <- glm(FDI.f ~ Distance +  PROJ_AGE_1_1 + DISTURBANCE_TYPE_1  + 
                        BURN_SEVERITY_RATING_1 + MEAN + SPECIES_CD_1_1 +SPECIES_CD_2_1 + SPECIES_CD_3_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
summary(structure.FDI.2a)

structure.FDI.2b <- glm(FDI.f ~ Distance +  PROJ_AGE_1_1 + 
                          BURN_SEVERITY_RATING_1 + MEAN + SPECIES_CD_1_1 +
                          SPECIES_CD_2_1 + SPECIES_CD_3_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
lrtest(structure.FDI.2a, structure.FDI.2b)

structure.FDI.2c <- glm(FDI.f ~ Distance +  PROJ_AGE_1_1 + DISTURBANCE_TYPE_1 +
                           MEAN + SPECIES_CD_1_1 +
                          SPECIES_CD_2_1 + SPECIES_CD_3_1 ,
    family=binomial(link = "logit"), data=bin_dis_GIS1)
lrtest(structure.FDI.2a, structure.FDI.2c)

##understand what lrt test is saying with null hypothesis here. null = restrictions are justified by data
```




```{r}
bin_dis_GIS1$linpred.GLM2a <- predict(logistic.GLM2a) # Estimated logit using the linear part
bin_dis_GIS1$yhat.GLM2a <- fitted(logistic.GLM2a) # Estimated probability using inverse logityhat values
bin_dis_GIS1$resid.GLM2a <- resid(logistic.GLM2a) # the deviances 

dim(bin_dis_GIS1)
names(bin_dis_GIS1)
head(bin_dis_GIS1) # Notice that the yhat.GLM1 values are bounded by 0 and 1 (are probabilities!)

# Graph of predicted probabilities ranges for dead versus alive
# Would like the dead=0 (it is alive) trees to have all low predicted prob(dead) 
# and the dead=1 (it is dead) trees to all have high predicted prob (dead). 
par(mfrow=c(1,1),mai=c(1,1,0.6,0.6),cex=0.8)
plot(bin_dis_GIS1$FDI.f,bin_dis_GIS1$yhat.GLM2a,pch=8,
  main="Model 1: Predicted Prob(dead)for Dead versus Alive",
  ylab="Predicted Prob(dead)", xlab="Dead (=1) or Alive (=0) as Recorded")
par(mfrow=c(1,1),mai=c(1,1,1,1),cex=1)
```

```{r}

```

