---
title: "Occurrence"
author: "Nat"
date: "2024-03-11"
output: html_document
---

# Load dataframes and packages

```{r}
#okay so there is an issue here after all because these tokens are changing
library(tidyverse)
regen <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Regen_2023_ALL.csv"
regen <- read.csv(regen)
site <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Site.csv"
site <- read.csv(site)
GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/GIS_fixed.csv"
GIS <- read.csv(GIS)
internal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Internal.csv"
internal <- read.csv(internal)
basal <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/BasalArea.csv"
basal <- read.csv(basal)
regen_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_GIS.csv"
regen_GIS <- read.csv(regen_GIS)
bin_GIS <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/binary_GIS.csv"
bin_GIS <- read.csv(bin_GIS)
regen_binary <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Dataframes/regen_binary.csv"
regen_binary <- read.csv(regen_binary)
actual_coords <- "https://raw.githubusercontent.com/nmac2000/Regen/main/Data/Plot_coordinates_actual.csv"
actual_coords <- read.csv(actual_coords)

```

# some plots (not that useful)

```{r}
#plots###############################################################################################
head(regen_GIS)
names(regen_GIS)


## Making plots. Need to make them look better


ggplot(regen_GIS, aes(x=PARENT_SOILS,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=Fire_Severity_1,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=Zone,y=total_count)) +
  geom_boxplot()

#will maybe have to combine some of these (what is PL)
ggplot(regen_GIS, aes(x=Species_1,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=DRAIN_1,y=total_count)) +
  geom_boxplot()

ggplot(regen_GIS, aes(x=DRAIN_1)) +
  geom_boxplot(aes(y=total_count), color="blue",position = "dodge") +
  geom_boxplot(aes(y=PLI_count), color = "red", position = "dodge")

ggplot(regen_GIS, aes(x=Solar_Radiation)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=TWI)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5) 

ggplot(regen_GIS, aes(x=COFRAG_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

#do as boxplot
ggplot(regen_GIS, aes(x=Aspect)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Severity_Patch_Size_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Age_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)  

ggplot(regen_GIS, aes(x=Height_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Crown_Closure_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Disturbance_Date_1)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

ggplot(regen_GIS, aes(x=Distance_to_Perimeter)) +
  geom_point(aes(y=PLI_count), color="red", alpha= .5) +
  geom_point(aes(y=FDI_count), color="green", alpha=.5)

```

# deliverables for Anya
making tables for different categorical variables and seeing how they have been sampled

```{r}
table(GIS$SOILNAME_1)
table(regen_GIS$SOILNAME_1)


compare_tables <- function(table1, table2, driver_column) {
  # Convert factor columns to characters
  table1[[driver_column]] <- as.character(table1[[driver_column]])
  table2[[driver_column]] <- as.character(table2[[driver_column]])
  
  # Use count function to get counts for each table
  count_table1 <- count(table1, !!as.name(driver_column))
  count_table2 <- count(table2, !!as.name(driver_column))
  
  # Combine counts using full join
  comparison_df <- full_join(count_table1, count_table2, by = driver_column)
  
  # Replace NAs with 0 in the count columns
  comparison_df[is.na(comparison_df)] <- 0
  
  # Return the comparison table
  return(comparison_df)
}

# usage:
driver_column_name <- c("Fire_Severity_1")  
result <- compare_tables(GIS, regen_GIS, driver_column_name)
print(result)


BEC_comparison <- compare_tables(GIS, regen_GIS, "Zone")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
ParentSoil_comparison <- compare_tables(GIS, regen_GIS, "PARENT_SOILS")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
SoilName_comparison  <- compare_tables(GIS, regen_GIS, "SOILNAME_1")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
Texture_comparison <- compare_tables(GIS, regen_GIS, "TEXTURE_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
Drainage_comparison  <- compare_tables(GIS, regen_GIS, "DRAIN_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
#two different rows with 0s
Cofrag_comparison  <- compare_tables(GIS, regen_GIS, "COFRAG_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100)
FireYear_comparison  <- compare_tables(GIS, regen_GIS, "Fire_Year_1")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%  
  filter(row_number() <= n()-1)
FireNum_comparison  <- compare_tables(GIS, regen_GIS, "Fire_Number_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/total_plots*100) %>% 
  filter(row_number() <= n()-1)
FireSeverity_comparison  <- compare_tables(GIS, regen_GIS, "Fire_Severity_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)




Overstory_comparison  <- compare_tables(GIS, regen_GIS, "Species_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
# Combine some of the Species for overstory
# PLI <- PL
# FDI <- FD
# Spruce <- SE, SX
# ??? <- B, EP, S


#
CrownClosure_comparison  <- compare_tables(GIS, regen_GIS, "Crown_Closure_1")%>%
  rename(total_plots = n.x, measured_plots = n.y) %>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) 
Disturbance_comparison  <- compare_tables(GIS, regen_GIS, "Disturbance_Type_1")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)
Subzone_comparison  <- compare_tables(GIS, regen_GIS, "Subzone")%>%
  rename(total_plots = n.x, measured_plots = n.y)%>% 
  mutate(PercentOfTotal = total_plots/sum(total_plots)*100) %>%
  mutate(PercentSampled = measured_plots/sum(measured_plots)*100) %>%
  filter(row_number() <= n()-1)

overstory_BEC <- GIS %>% 
  group_by(Zone, Species_1) %>% 
  summarize(n())




```
####overstory and BEC

# Continuation of deliverables for Anya
this looks at occurrence and basic stocking for some of the categorical data
```{r}
#deliverables#################################################
#Anya wants conifer count
#Fire severity
regen_FS <- regen_GIS %>% 
  select(Card:Spruce_x130,Fire_Severity_1) %>% 
  group_by(Fire_Severity_1) %>% 
  filter(!is.na(Fire_Severity_1))

regen_FS$Con_count <- regen_FS$FDI_count + regen_FS$PLI_count + regen_FS$Spruce_count
regen_FS$Con_tph <- regen_FS$Con_count*200

options(pillar.sigfig = 6) 

regen_FS %>% 
  summarise(across(c(31,32), sd))

regen_FS %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_FS %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_FS) +
  geom_histogram(aes(x = Con_count, fill = Fire_Severity_1), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Fire_Severity_1))

#write.csv(FireSeverity_comparison, "C:/Users/nmac2000/Documents/regen project/Data/FireSeverity.csv")

#BEC zones
regen_BEC <- regen_GIS %>% 
  select(Card:Spruce_x130,Zone) %>% 
  group_by(Zone) %>% 
  filter(!is.na(Zone))

regen_BEC$Con_count <- regen_BEC$FDI_count + regen_BEC$PLI_count + regen_BEC$Spruce_count
regen_BEC$Con_tph <- regen_BEC$Con_count*200

options(pillar.sigfig = 6) 

regen_BEC %>% 
  summarise(across(c(31,32), sd))

regen_BEC %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_BEC %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_BEC) +
  geom_histogram(aes(x = Con_count, fill = Zone), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Zone))


## add subzone
regen_subzone <- regen_GIS %>% 
  select(Card:Spruce_x130,Zone,Subzone) %>% 
  group_by(Zone,Subzone) %>% 
  filter(!is.na(Zone))

regen_subzone$Con_count <- regen_BEC$FDI_count + regen_BEC$PLI_count + regen_BEC$Spruce_count
regen_subzone$Con_tph <- regen_BEC$Con_count*200

options(pillar.sigfig = 6) 

regen_subzone %>% 
  summarise(across(c(31,32), sd))

regen_subzone %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_subzone %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_subzone) +
  geom_histogram(aes(x = Con_count, fill = Subzone), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Subzone))

#Overstory


regen_Overstory <- regen_GIS %>% 
  select(Card:Spruce_x130,Species_1) %>% 
  group_by(Species_1) %>% 
  filter(!is.na(Species_1))

regen_Overstory$Species_1 <- sub("\\bSX\\b", "Spruce", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bS\\b", "Spruce", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bSE\\b", "Spruce", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bPL\\b", "PLI", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bFD\\b", "FDI", regen_Overstory$Species_1)
regen_Overstory$Species_1 <- sub("\\bPA\\b", "PLI", regen_Overstory$Species_1)

regen_Overstory$Con_count <- regen_Overstory$FDI_count + regen_Overstory$PLI_count + regen_Overstory$Spruce_count
regen_Overstory$Con_tph <- regen_Overstory$Con_count*200

options(pillar.sigfig = 6) 

regen_Overstory %>% 
  summarise(across(c(31,32), sd))

regen_Overstory %>% 
  filter(Con_count > 0) %>%
  summarise(count = n())


regen_Overstory %>% 
  summarise(percentage = sum(PLI_count > 5) / n() * 100)

ggplot(regen_Overstory) +
  geom_histogram(aes(x = Con_count, fill = Species_1), alpha = 0.7, binwidth = 50) +
  labs(x = "Conifer Seedlings per Plot", y = "Frequency", title = "Distribution of Conifer Seedlings per Plot") +
  theme_minimal() +
  facet_wrap(vars(Species_1))
```

#Which plots have unknown burn severity
```{r}
for_table <- regen_GIS %>% 
  filter(Fire_Severity_1 == "Unknown") %>% 
  select(Card, Fire_Year_1, Fire_Year_2, Fire_Severity_1, Fire_Severity_2, Fire_Number_1, Fire_Number_2, Longitude, Latitude)

#write.csv(for_table, "C:/Users/nmac2000/Documents/regen project/Data/Unknown_Severity_Measured_Plots.csv")

```

# Looking at wedge data (Bianca said this isnt useful)
```{r}
#Wedges###############################
# now i want to have columns for each species
regen_wedge <- regen
regen_wedge$FDI_total <- ifelse(regen_wedge$Species == "FDI", regen_wedge$total, 0)
regen_wedge$FDI_x0 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x0, 0)
regen_wedge$FDI_x10 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x10, 0)
regen_wedge$FDI_x30 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x30, 0)
regen_wedge$FDI_x130 <- ifelse(regen_wedge$Species == "FDI", regen_wedge$x130, 0)
regen_wedge$PLI_total <- ifelse(regen_wedge$Species == "PLI", regen_wedge$total, 0)
regen_wedge$PLI_x0 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x0, 0)
regen_wedge$PLI_x10 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x10, 0)
regen_wedge$PLI_x30 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x30, 0)
regen_wedge$PLI_x130 <- ifelse(regen_wedge$Species == "PLI", regen_wedge$x130, 0)
regen_wedge$NonCon_total <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$total, 0)
regen_wedge$NonCon_x0 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x0, 0)
regen_wedge$NonCon_x10 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x10, 0)
regen_wedge$NonCon_x30 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x30, 0)
regen_wedge$NonCon_x130 <- ifelse(regen_wedge$Species == "NonCon", regen_wedge$x130, 0)
regen_wedge$Spruce_total <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$total, 0)
regen_wedge$Spruce_x0 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x0, 0)
regen_wedge$Spruce_x10 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x10, 0)
regen_wedge$Spruce_x30 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x30, 0)
regen_wedge$Spruce_x130 <- ifelse(regen_wedge$Species == "Spruce", regen_wedge$x130, 0)


# remove NR rows for plots that have other species present
regen_wedge <- regen_wedge %>% 
  group_by(Card) %>% 
  mutate(has_nr = any(Species == "NR"), num_rows = n()) %>% 
  filter(num_rows == 1 | !(has_nr & Species == "NR")) %>% 
  select(-has_nr, -num_rows) %>% 
  select(-Plot_Sp)

#regen_wedge <- regen_wedge %>% 
  rename("total_x0" = "x0",
         "total_x10" = "x10",
         "total_x30" = "x30",
         "total_x130" = "x130",
         "total_count" = "total")




regen_wedge1 <- regen_wedge %>% 
  group_by(Card, Quandrant) %>% 
  summarize(SpeciesAll = paste(Species, collapse = ", "),
            total_count = sum(total),
            total_tph = total_count*200,
            total_x0 = sum(x0),
            total_x10 = sum(x10),
            total_x30 = sum(x30),
            total_x130 = sum(x130),
            FDI_count = sum(FDI_total),
            FDI_tph = FDI_count*200,
            FDI_x0 = sum(FDI_x0),
            FDI_x10 = sum(FDI_x10),
            FDI_x30 = sum(FDI_x30),
            FDI_x130 = sum(FDI_x130),
            PLI_count = sum(PLI_total),
            PLI_tph = PLI_count*200,
            PLI_x0 = sum(PLI_x0),
            PLI_x10 = sum(PLI_x10),
            PLI_x30 = sum(PLI_x30),
            PLI_x130 = sum(PLI_x130),
            NonCon_count = sum(NonCon_total),
            NonCon_x0 = sum(NonCon_x0),
            NonCon_x10 = sum(NonCon_x10),
            NonCon_x30 = sum(NonCon_x30),
            NonCon_x130 = sum(NonCon_x130),
            Spruce_count = sum(Spruce_total),
            Spruce_x0 = sum(Spruce_x0),
            Spruce_x10 = sum(Spruce_x10),
            Spruce_x30 = sum(Spruce_x30),
            Spruce_x130 = sum(Spruce_x130)) %>% 
  ungroup()



test <- regen_wedge1 %>% 
  group_by(Card) %>% 
  summarize(total_sd = sqrt(sum((total_count-sum(total_count)/4)^2)/3),
            PLI_sd = sqrt(sum((PLI_count-sum(PLI_count)/4)^2)/3),
            FDI_sd = sqrt(sum((FDI_count-sum(FDI_count)/4)^2)/3))

options(scipen=999)

test <- test %>%
  gather(key = "Species", value = "SD", total_sd, PLI_sd, FDI_sd)

ggplot(data=test, aes(x = SD, fill = Species)) +
  geom_histogram(position = "dodge", bins = 30, color = "white", alpha = 0.7) +
  facet_wrap(~Species) +
  theme_minimal() +
  labs(x="SD (Seedlings per plot)", y="Frequency", title="In Plot Variability") +
  scale_fill_discrete()

ggplot(data=filter(test, SD > 0), aes(x = SD, fill = Species)) +
  geom_histogram(position = "dodge", bins = 30, color = "white", alpha = 0.7) +
  facet_wrap(~Species) +
  theme_minimal() +
  labs(x="SD (Seedlings per plot)", y="Frequency", title="In Plot Variability") +
  scale_fill_discrete()

options(scipen=0)

```



#Some graphs with binary
```{r}
#Making graphs
##aspect and total count (no real change IMO)
aspect_graph <- bin_GIS %>%
  group_by(Azimuth, total_count_bin) %>%
  summarise(count = n()) 

aspect_graph <- aspect_graph %>%
  group_by(Azimuth) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$total_count_bin <- as.factor(aspect_graph$total_count_bin)  

ggplot(filter(aspect_graph, !is.na(Azimuth)), aes(x = Azimuth, y = percentage, fill = total_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "Total Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and Total Count Bin") +
  theme_minimal() 
 
ggplot(filter(aspect_graph, !is.na(Azimuth)), aes(x = Azimuth, y = count, fill = total_count_bin)) +
  geom_col(position="dodge") +  # Adjust dodge width as needed # Adjust colors as needed
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "Total Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Count", 
       title = "Count of Observations by Aspect Category and Total Count Bin") +
  theme_minimal() 

#PLI abd aspect
aspect_graph <- bin_GIS %>%
  group_by(Azimuth, PLI_count_bin) %>%
  summarise(count = n()) 


aspect_graph <- aspect_graph %>%
  group_by(Azimuth) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$PLI_count_bin <- as.factor(aspect_graph$PLI_count_bin)  

ggplot(filter(aspect_graph, !is.na(Azimuth)), aes(x = Azimuth, y = percentage, fill = PLI_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "PLI Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and PLI Count Bin") +
  theme_minimal() 

#FDI and aspect
aspect_graph <- bin_GIS %>%
  group_by(Azimuth, FDI_count_bin) %>%
  summarise(count = n()) 


aspect_graph <- aspect_graph %>%
  group_by(Azimuth) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$FDI_count_bin <- as.factor(aspect_graph$FDI_count_bin)  

ggplot(filter(aspect_graph, !is.na(Azimuth)), aes(x = Azimuth, y = percentage, fill = FDI_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "FDI Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and FDI Count Bin") +
  theme_minimal() 

#NonCon and aspect
aspect_graph <- bin_GIS %>%
  group_by(Azimuth, NonCon_count_bin) %>%
  summarise(count = n()) 


aspect_graph <- aspect_graph %>%
  group_by(Azimuth) %>%
  mutate(percentage = count / sum(count) * 100)

aspect_graph$NonCon_count_bin <- as.factor(aspect_graph$NonCon_count_bin)  

ggplot(filter(aspect_graph, !is.na(Azimuth)), aes(x = Azimuth, y = percentage, fill = NonCon_count_bin)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("#E41A1C", "#4DAF4A"), 
                    name = "NonCon Count Bin",
                    labels = c("No regen", "Regen")) +
  labs(x = "Aspect Category", y = "Percentage", 
       title = "Percentage of Observations by Aspect Category and NonCon Count Bin") +
  theme_minimal() 



#next lets try getting them all on the same plot
```

# Occurrence as binary plot

```{r}

names(regen_binary)
regen_for_table <- regen_binary %>% 
  summarise(total_no_occurrence = n()-sum(total_count_bin),
            x0_no_occurrence = n()-sum(total_x0_bin),
            x10_no_occurrence = n()-sum(total_x10_bin),
            x30_no_occurrence = n()-sum(total_x30_bin),
            x130_no_occurrence = n()-sum(total_x130_bin),
            FDI_count_occurrence = sum(FDI_count_bin),
            FDI_x0_occurrence = sum(FDI_x0_bin),
            FDI_x10_occurrence = sum(FDI_x10_bin),
            FDI_x30_occurrence = sum(FDI_x30_bin),
            FDI_x130_occurrence = sum(FDI_x130_bin),
            PLI_count_occurrence = sum(PLI_count_bin),
            PLI_x0_occurrence = sum(PLI_x0_bin),
            PLI_x10_occurrence = sum(PLI_x10_bin),
            PLI_x30_occurrence = sum(PLI_x30_bin),
            PLI_x130_occurrence = sum(PLI_x130_bin),
            NonCon_count_occurrence = sum(NonCon_count_bin),
            NonCon_x0_occurrence = sum(NonCon_x0_bin),
            NonCon_x10_occurrence = sum(NonCon_x10_bin),
            NonCon_x30_occurrence = sum(NonCon_x30_bin),
            NonCon_x130_occurrence = sum(NonCon_x130_bin),
            Spruce_count_occurrence = sum(Spruce_count_bin),
            Spruce_x0_occurrence = sum(Spruce_x0_bin),
            Spruce_x10_occurrence = sum(Spruce_x10_bin),
            Spruce_x30_occurrence = sum(Spruce_x30_bin),
            Spruce_x130_occurrence = sum(Spruce_x130_bin)
            )

regen_table <- gather(regen_for_table, "AgeClass", "Count",1:25)
regen_table$Species <- c("No Regen","No Regen","No Regen","No Regen","No Regen","FDI","FDI",
                         "FDI","FDI","FDI","PLI","PLI","PLI","PLI","PLI","Non Conifer",
                         "Non Conifer","Non Conifer","Non Conifer","Non Conifer", 
                         "Spruce","Spruce","Spruce","Spruce", "Spruce")
regen_table$AgeClass <- c("All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130",
                          "All heights", "x0", "x10", "x30", "x130")

class_order <- c("All heights", "x0", "x10", "x30", "x130")
species_order <- c("PLI","FDI","Spruce","Non Conifer","No Regen")
ggplot(regen_table, aes(x = factor(AgeClass, levels = class_order), y = Count)) +
  geom_col(aes(fill = factor(Species, levels = species_order)), position = "dodge") +
  xlab("Height Class (cm)") +
  ylab("# of Plots with Occurrence") +
  ggtitle("Occurrence of Regen by Height Class and Species") +
  labs(fill = "Species") +
  scale_fill_brewer(palette = "Spectral") +
  scale_x_discrete(labels = c("total" = "All heights", "x0" = "0-9", "x10" = "10-29", "x30" = "30-129", "x130" = "130+")) +
  theme_bw() +
  theme(axis.text.x=element_text(size=15),
        axis.text.y=element_text(size=15),
        axis.title.x=element_text(size=20),
        axis.title.y=element_text(size=20),
        plot.title = element_text(size = 20),
        legend.text = element_text(size=15),
        legend.title = element_text(size=20))
```



I want to make a graph that has an explanatory categorical variable on the x axis and counts of plots on the y axis. Each category will have 2 bars, one for 0s one for 1s
```{r}
##Parent Soils
bin_GIS_plot <- bin_GIS %>%
  group_by(PARENT_SOILS, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = PARENT_SOILS, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

##Azimuth
bin_GIS_plot <- bin_GIS %>%
  group_by(Azimuth, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = Azimuth, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

##Texture
bin_GIS_plot <- bin_GIS %>%
  group_by(TEXTURE_1, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = TEXTURE_1, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

##DRAIN_1
bin_GIS_plot <- bin_GIS %>%
  group_by(DRAIN_1, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = DRAIN_1, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

##BEC
bin_GIS_plot <- bin_GIS %>%
  group_by(Zone, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = Zone, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

##Coarse Fragment
bin_GIS_plot <- bin_GIS %>%
  group_by(PERCENT_1, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = PERCENT_1, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


##Coarse Fragment
bin_GIS_plot <- bin_GIS %>%
  group_by(PERCENT_1, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = PERCENT_1, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


##Fire Severity
bin_GIS_plot <- bin_GIS %>%
  group_by(Fire_Severity_1, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = Fire_Severity_1, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "salmon", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


##Disturbance
bin_GIS_plot <- bin_GIS %>%
  group_by(Disturbance_Type_1, total_count_bin) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count))

# Plot the proportions
ggplot(bin_GIS_plot, aes(x = Disturbance_Type_1, y = proportion, fill = factor(total_count_bin))) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Explanatory Categorical Variable", y = "Proportion of Plots",
       fill = "Regeneration Presence") +
  scale_fill_manual(values = c("0" = "darkseagreen", "1" = "darkslategray4"),
                    labels = c("0" = "No regeneration",
                               "1" = "Regeneration")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
forcoords <- regen_GIS %>% 
  select(Card, Fire_Year_1, Fire_Number_1)
actual_coords <- rename(actual_coords, Card = Plot.ID)
forSasha <- full_join(forcoords, actual_coords, by="Card")
#write.csv(forSasha,  "C:/Users/nmac2000/Documents/regen project/Data/ForSasha.csv")
```

```{r}
for_export <- regen_binary %>% 
  select(Card, FDI_count_bin, PLI_count_bin, Spruce_count_bin) %>% 
  rename("Plot ID" = "Card")
for_export <- full_join(Plot_coordinates_actual, for_export, by="Plot ID")
for_file <- regen_GIS %>% 
  select(Card, Species_1, Elevation,Fire_Year_1,Fire_Year_2) 

for_file <- full_join(for_file, site, by ="Card")

for_export <- full_join(for_export, for_file, by = "Plot ID")
write.csv(for_export,  "/Users/natalie/Documents/Regen/Regen/Data/for_export.csv")
write.csv(for_file,  "/Users/natalie/Documents/Regen/Regen/Data/plot_info.csv")
regen_GIS %>%
  filter(Card == 1425)
```

